### 2020-01-23 paper.tex
Add ets Disclaimer and Attribution info

%
% File acl2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{Instructions for ACL 2020 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
This document contains the instructions for preparing a manuscript for the proceedings of ACL 2020.
The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
These instructions should be used for both papers submitted for review and for final versions of accepted papers.
Authors are asked to conform to all the directions reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted
by Steven Bethard, Ryan Cotterrell and Rui Yan
from the instructions for earlier ACL and NAACL proceedings, including those for 
ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
NAACL 2018 by Margaret Michell and Stephanie Lukin,
2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan, 
NAACL 2017 by Margaret Mitchell, 
ACL 2012 by Maggie Li and Michael White, 
ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
ACL 2002 by Eugene Charniak and Dekang Lin, 
and earlier ACL and EACL formats written by several people, including
John Chen, Henry S. Thompson and Donald Walker.
Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.

\section{Introduction}

The following instructions are directed to authors of papers submitted to ACL 2020 or accepted for publication in its proceedings.
All authors are required to adhere to these specifications.
Authors are required to provide a Portable Document Format (PDF) version of their papers.
\textbf{The proceedings are designed for printing on A4 paper.}

\section{Electronically-available resources}

ACL provides this description and accompanying style files at
\begin{quote}
\url{http://acl2020.org/downloads/acl2020-templates.zip}
\end{quote}
We strongly recommend the use of these style files, which have been appropriately tailored for the ACL 2020 proceedings.

\paragraph{\LaTeX-specific details:}
The templates include the \LaTeX2e{} source (\texttt{\small acl2020.tex}),
the \LaTeX2e{} style file used to format it (\texttt{\small acl2020.sty}),
an ACL bibliography style (\texttt{\small acl\_natbib.bst}),
an example bibliography (\texttt{\small acl2020.bib}),
and the bibliography for the ACL Anthology (\texttt{\small anthology.bib}).

\section{Length of Submission}
\label{sec:length}

The conference accepts submissions of long papers and short papers.
Long papers may consist of up to eight (8) pages of content plus unlimited pages for references.
Upon acceptance, final versions of long papers will be given one additional page -- up to nine (9) pages of content plus unlimited pages for references -- so that reviewers' comments can be taken into account.
Short papers may consist of up to four (4) pages of content, plus unlimited pages for references.
Upon acceptance, short papers will be given five (5) pages in the proceedings and unlimited pages for references. 
For both long and short papers, all illustrations and tables that are part of the main text must be accommodated within these page limits, observing the formatting instructions given in the present document.
Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.

The conference encourages the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.
Additional material must be submitted as separate files, and must adhere to the same anonymity guidelines as the main paper.
The paper must be self-contained: it is optional for reviewers to look at the supplementary material.
Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers.
Refer to Appendices~\ref{sec:appendix} and \ref{sec:supplemental} for further information.

Workshop chairs may have different rules for allowed length and whether supplemental material is welcome.
As always, the respective call for papers is the authoritative source.

\section{Anonymity}
As reviewing will be double-blind, papers submitted for review should not include any author information (such as names or affiliations). Furthermore, self-references that reveal the author's identity, \emph{e.g.},
\begin{quote}
We previously showed \citep{Gusfield:97} \ldots
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
\citet{Gusfield:97} previously showed\ldots
\end{quote}
Please do not use anonymous citations and do not include acknowledgements.
\textbf{Papers that do not conform to these requirements may be rejected without review.}

Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
Reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.

Once a paper has been accepted to the conference, the camera-ready version of the paper should include the author's names and affiliations, and is allowed to use self-references.

\paragraph{\LaTeX-specific details:}
For an anonymized submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is commented out, and that you have filled in the paper ID number (assigned during the submission process on softconf) where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top of this document.
For a camera-ready submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is not commented out.

\section{Multiple Submission Policy}
Papers that have been or will be submitted to other meetings or publications must indicate this at submission time in the START submission form, and must be withdrawn from the other venues if accepted by ACL 2020. Authors of papers accepted for presentation at ACL 2020 must notify the program chairs by the camera-ready deadline as to whether the paper will be presented. We will not accept for publication or presentation the papers that overlap significantly in content or results with papers that will be (or have been) published elsewhere.

Authors submitting more than one paper to ACL 2020 must ensure that submissions do not overlap significantly (>25\%) with each other in content or results.

\section{Formatting Instructions}

Manuscripts must be in two-column format.
Exceptions to the two-column format include the title, authors' names and complete addresses, which must be centered at the top of the first page, and any full-width figures or tables (see the guidelines in Section~\ref{ssec:title-authors}).
\textbf{Type single-spaced.}
Start all pages directly under the top margin.
The manuscript should be printed single-sided and its length should not exceed the maximum page limit described in Section~\ref{sec:length}.
Pages should be numbered in the version submitted for review, but \textbf{pages should not be numbered in the camera-ready version}.

\paragraph{\LaTeX-specific details:}
The style files will generate page numbers when {\small\verb|\aclfinalcopy|} is commented out, and remove them otherwise.

\subsection{File Format}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's Portable Document Format (PDF).
Please make sure that your PDF file includes all the necessary fonts (especially tree diagrams, symbols, and fonts with Asian characters).
When you print or create the PDF file, there is usually an option in your printer setup to include none, all or just non-standard fonts.
Please make sure that you select the option of including ALL the fonts.
\textbf{Before sending it, test your PDF by printing it from a computer different from the one where it was created.}
Moreover, some word processors may generate very large PDF files, where each page is rendered as an image.
Such images may reproduce poorly.
In this case, try alternative ways to obtain the PDF.
One way on some systems is to install a driver for a postscript printer, send your document to the printer specifying ``Output to a file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm x 29.7 cm) when formatting the paper.
Print-outs of the PDF file on A4 paper should be identical to the hardcopy version.
If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs as soon as possible.

\paragraph{\LaTeX-specific details:}
PDF files are usually produced from \LaTeX{} using the \texttt{\small pdflatex} command.
If your version of \LaTeX{} produces Postscript files, \texttt{\small ps2pdf} or \texttt{\small dvipdf} can convert these to PDF.
To ensure A4 format in \LaTeX, use the command {\small\verb|\special{papersize=210mm,297mm}|}
in the \LaTeX{} preamble (below the {\small\verb|\usepackage|} commands) and use \texttt{\small dvipdf} and/or \texttt{\small pdflatex}; or specify \texttt{\small -t a4} when working with \texttt{\small dvips}.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted.
The exact dimensions for a page on A4 paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's \textbf{Times Roman} font should be used.
If Times Roman is unavailable, you may use Times New Roman or \textbf{Computer Modern Roman}.

Table~\ref{font-table} specifies what font sizes and styles must be used for each type of text in the manuscript.

\begin{table}
\centering
\begin{tabular}{lrl}
\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
subsection titles & 11 pt & bold \\
document text & 11 pt  &\\
captions & 10 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\caption{\label{font-table} Font guide. }
\end{table}

\paragraph{\LaTeX-specific details:}
To use Times Roman in \LaTeX2e{}, put the following in the preamble:
\begin{quote}
\small
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}

\subsection{Ruler}
A printed ruler (line numbers in the left and right margins of the article) should be presented in the version submitted for review, so that reviewers may comment on particular lines in the paper without circumlocution.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera ready copy should not contain a ruler.

\paragraph{Reviewers:}
note that the ruler measurements may not align well with lines in the paper -- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
In most cases one would expect that the approximate location will be adequate, although you can also use fractional references (\emph{e.g.}, this line ends at mark $295.5$).

\paragraph{\LaTeX-specific details:}
The style files will generate the ruler when {\small\verb|\aclfinalcopy|} is commented out, and remove it otherwise.

\subsection{Title and Authors}
\label{ssec:title-authors}

Center the title, author's name(s) and affiliation(s) across both columns.
Do not use footnotes for affiliations.
Place the title centered at the top of the first page, in a 15-point bold font.
Long titles should be typed on two lines without a blank line intervening.
Put the title 2.5 cm from the top of the page, followed by a blank line, then the author's names(s), and the affiliation on the following line.
Do not use only initials for given names (middle initials are allowed).
Do not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not ``MITCHELL'').
Do not format title and section headings in all capitals except for proper names (such as ``BLEU'') that are
conventionally in all capitals.
The affiliation should contain the author's complete address, and if possible, an electronic mail address.

The title, author names and addresses should be completely identical to those entered to the electronical paper submission website in order to maintain the consistency of author information among all publications of the conference.
If they are different, the publication chairs may resolve the difference without consulting with you; so it is in your own interest to double-check that the information is consistent.

Start the body of the first page 7.5 cm from the top of the page.
\textbf{Even in the anonymous version of the paper, you should maintain space for names and addresses so that they will fit in the final (accepted) version.}

\subsection{Abstract}
Use two-column format when you begin the abstract.
Type the abstract at the beginning of the first column.
The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by 0.6 cm on each side.
Center the word \textbf{Abstract} in a 12 point bold font above the body of the abstract.
The abstract should be a concise summary of the general thesis and conclusions of the paper.
It should be no longer than 200 words.
The abstract text should be in 10 point font.

\subsection{Text}
Begin typing the main body of the text immediately after the abstract, observing the two-column format as shown in the present document.

Indent 0.4 cm when starting a new paragraph.

\subsection{Sections}

Format section and subsection headings in the style shown on the present document.
Use numbered sections (Arabic numerals) to facilitate cross references.
Number subsections with the section number and the subsection number separated by a dot, in Arabic numerals.

\subsection{Footnotes}
Put footnotes at the bottom of the page and use 9 point font.
They may be numbered or referred to by asterisks or other symbols.\footnote{This is how a footnote should appear.}
Footnotes should be separated from the text by a line.\footnote{Note the line separating the footnotes from the text.}

\subsection{Graphics}

Place figures, tables, and photographs in the paper near where they are first discussed, rather than at the end, if possible.
Wide illustrations may run across both columns.
Color is allowed, but adhere to Section~\ref{ssec:accessibility}'s guidelines on accessibility.

\paragraph{Captions:}
Provide a caption for every illustration; number each one sequentially in the form:
``Figure 1. Caption of the Figure.''
``Table 1. Caption of the Table.''
Type the captions of the figures and tables below the body, using 10 point text.
Captions should be placed below illustrations.
Captions that are one line are centered (see Table~\ref{font-table}).
Captions longer than one line are left-aligned (see Table~\ref{tab:accents}).

\begin{table}
\centering
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular}
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\
\hline
\end{tabular}
\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\paragraph{\LaTeX-specific details:}
The style files are compatible with the caption and subcaption packages; do not add optional arguments.
\textbf{Do not override the default caption sizes.}

\subsection{Hyperlinks}
Within-document and external hyperlinks are indicated with Dark Blue text, Color Hex \#000099.

\subsection{Citations}
Citations within the text appear in parentheses as~\citep{Gusfield:97} or, if the author's name appears in the text itself, as \citet{Gusfield:97}.
Append lowercase letters to the year in cases of ambiguities.  
Treat double authors as in~\citep{Aho:72}, but write as in~\citep{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\citep{Gusfield:97,Aho:72}.

Refrain from using full citations as sentence constituents.
Instead of
\begin{quote}
  ``\citep{Gusfield:97} showed that ...''
\end{quote}
write
\begin{quote}
``\citet{Gusfield:97} showed that ...''
\end{quote}

\begin{table*}
\centering
\begin{tabular}{lll}
\hline
\textbf{Output} & \textbf{natbib command} & \textbf{Old ACL-style command}\\
\hline
\citep{Gusfield:97} & \small\verb|\citep| & \small\verb|\cite| \\
\citealp{Gusfield:97} & \small\verb|\citealp| & no equivalent \\
\citet{Gusfield:97} & \small\verb|\citet| & \small\verb|\newcite| \\
\citeyearpar{Gusfield:97} & \small\verb|\citeyearpar| & \small\verb|\shortcite| \\
\hline
\end{tabular}
\caption{\label{citation-guide}
Citation commands supported by the style file.
The style is based on the natbib package and supports all natbib citation commands.
It also supports commands defined in previous ACL style files for compatibility.
}
\end{table*}

\paragraph{\LaTeX-specific details:}
Table~\ref{citation-guide} shows the syntax supported by the style files.
We encourage you to use the natbib styles.
You can use the command {\small\verb|\citet|} (cite in text) to get ``author (year)'' citations as in \citet{Gusfield:97}.
You can use the command {\small\verb|\citep|} (cite in parentheses) to get ``(author, year)'' citations as in \citep{Gusfield:97}.
You can use the command {\small\verb|\citealp|} (alternative cite without  parentheses) to get ``author year'' citations (which is useful for  using citations within parentheses, as in \citealp{Gusfield:97}).

\subsection{References}
Gather the full set of references together under the heading \textbf{References}; place the section before any Appendices. 
Arrange the references alphabetically by first author, rather than by order of occurrence in the text.

Provide as complete a citation as possible, using a consistent format, such as the one for \emph{Computational Linguistics\/} or the one in the  \emph{Publication Manual of the American 
Psychological Association\/}~\citep{APA:83}.
Use full names for authors, not just initials.

Submissions should accurately reference prior and related work, including code and data.
If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
If multiple versions of a piece of prior work exist, the one used by the authors should be referenced.
Authors should not rely on automated citation indices to provide accurate references for prior and related work.

The following text cites various types of articles so that the references section of the present document will include them.
\begin{itemize}
\item Example article in journal: \citep{Ando2005}.
\item Example article in proceedings, with location: \citep{borschinger-johnson-2011-particle}.
\item Example article in proceedings, without location: \citep{andrew2007scalable}.
\item Example arxiv paper: \citep{rasooli-tetrault-2015}. 
\end{itemize}

\paragraph{\LaTeX-specific details:}
The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
If your own bib file is named \texttt{\small acl2020.bib}, then placing the following before any appendices in your \LaTeX{}  file will generate the references section for you:
\begin{quote}\small
\verb|\bibliographystyle{acl_natbib}|\\
\verb|\bibliography{acl2020}|
\end{quote}

You can obtain the complete ACL Anthology as a Bib\TeX\ file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
To include both the anthology and your own bib file, use the following instead of the above.
\begin{quote}\small
\verb|\bibliographystyle{acl_natbib}|\\
\verb|\bibliography{anthology,acl2020}|
\end{quote}

\subsection{Digital Object Identifiers}
As part of our work to make ACL materials more widely used and cited outside of our discipline, ACL has registered as a CrossRef member, as a registrant of Digital Object Identifiers (DOIs), the standard for registering permanent URNs for referencing scholarly materials.

All camera-ready references are required to contain the appropriate DOIs (or as a second resort, the hyperlinked ACL Anthology Identifier) to all cited works.
Appropriate records should be found for most materials in the current ACL Anthology at \url{http://aclanthology.info/}.
As examples, we cite \citep{goodman-etal-2016-noise} to show you how papers with a DOI will appear in the bibliography.
We cite \citep{harper-2014-learning} to show how papers without a DOI but with an ACL Anthology Identifier will appear in the bibliography.

\paragraph{\LaTeX-specific details:}
Please ensure that you use Bib\TeX\ records that contain DOI or URLs for any of the ACL materials that you reference.
If the Bib\TeX{} file contains DOI fields, the paper title in the references section will appear as a hyperlink to the DOI, using the hyperref \LaTeX{} package.

\subsection{Appendices}
Appendices, if any, directly follow the text and the
references (but only in the camera-ready; see Appendix~\ref{sec:appendix}).
Letter them in sequence and provide an informative title:
\textbf{Appendix A. Title of Appendix}.

\section{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate people who are color-blind (as well as those printing to paper), grayscale readability is strongly encouraged.
Color is not forbidden, but authors should ensure that tables and figures do not rely solely on color to convey critical distinctions.
A simple criterion:
All curves and points in your figures should be clearly distinguishable without color.

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms with appropriate transliterations and/or translations since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in the order of:
\begin{center}
\begin{tabular}{c}
original-form \\
transliteration \\
``translation''
\end{tabular}
\end{center}

\section{\LaTeX{} Compilation Issues}
You may encounter the following error during compilation: 
\begin{quote}
{\small\verb|\pdfendlink|} ended up in different nesting level than {\small\verb|\pdfstartlink|}.
\end{quote}
This happens when \texttt{\small pdflatex} is used and a citation splits across a page boundary.
To fix this, the style file contains a patch consisting of two lines:
(1) {\small\verb|\RequirePackage{etoolbox}|} (line 455 in \texttt{\small acl2020.sty}), and
(2) A long line below (line 456 in \texttt{\small acl2020.sty}).

If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \texttt{\small hyperref} package by loading the style file with the \texttt{\small nohyperref} option:

\noindent
{\small\verb|\usepackage[nohyperref]{acl2020}|}

\noindent
Then recompile, find the problematic citation, and rewrite the sentence containing the citation. (See, {\em e.g.}, \url{http://tug.org/errors.html})

\section*{Acknowledgments}

The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
Do not include this section when submitting your paper for review.

Attributions.
In the event that Researcher produces a written work that incorporates the
Results or limited excerpts of the Data (with prior written consent from ETS),
Researcher agrees to acknowledge the Data as property of ETS by displaying the
following attributions:

Source: 
Derived from data provided by ETS. Copyright \textcopyright{}2020 ETS,
\url{www.ets.org}.

Disclaimer.
Researcher must also include the following disclaimer language in all publications:  
The opinions set forth in this publication are those of the author(s) and not ETS.

\bibliography{anthology,acl2020}
\bibliographystyle{acl_natbib}

\appendix

\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Submissions may include non-readable supplementary material used in the work and described in the paper.
Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
\textbf{Submissions that misuse the supplementary material may be rejected without review.}
Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
(Source code and data should be separate uploads, rather than part of the paper).

The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.

\end{document}

### 2020-05-16 paper.tex
Fix missing space
Update on Overleaf.

@@
 
+%%% by estemle
+\usepackage[utf8x]{inputenc}
+\usepackage[autostyle=none]{csquotes}
+\usepackage{tabularx}
+\usepackage{graphicx}
+\usepackage{multirow}
+\usepackage{siunitx}
+\sisetup{input-ignore={,},group-separator={,},input-decimal-markers={.}}
+\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}
+
 %\aclfinalcopy % Uncomment this line for the final submission
@@
 
-\title{Instructions for ACL 2020 Proceedings}
+\title{Testing the role of metadata in a neural network architecture of metaphor identification}
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\}
+\author{Egon W.~Stemle \\
+  Eurac Research / Bolzano-Bozen (IT) \\
+  Masaryk University / Brno (CZ) \\
+  {\tt egon.stemle@eurac.edu} \\\And
+  Alexander Onysko \\
+  University of  Klagenfurt / Klagenfurt (AT) \\
+  {\tt alexander.onysko@aau.at} \\}
 
@@
 \begin{abstract}
-This document contains the instructions for preparing a manuscript for the proceedings of ACL 2020.
-The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
-These instructions should be used for both papers submitted for review and for final versions of accepted papers.
-Authors are asked to conform to all the directions reported in this document.
+This paper describes the application of a neural network for the automatic detection of metaphors.
+The system participated in the shared task of metaphor identification that is part of the Second Workshop of Figurative Language Processing held at ACL 2020.
+The particular focus of our approach is on the potential influence that the metadata given in the ETS Corpus of Non-Native Written English might have on the automatic detection of metaphors in this dataset.
+The article first discusses the annotated ETS learner data, highlighting some of its peculiarities and inherent biases of metaphor use.
+This is followed by a series of evaluations performed by an LSTM BiRNN classification architecture in order to test whether specific metadata have an influence on the system performance in this task of automated metaphor identification.
 \end{abstract}
-
-\section{Credits}
-
-This document has been adapted
-by Steven Bethard, Ryan Cotterrell and Rui Yan
-from the instructions for earlier ACL and NAACL proceedings, including those for 
-ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
-NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
-ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
-NAACL 2018 by Margaret Michell and Stephanie Lukin,
-2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
-ACL 2017 by Dan Gildea and Min-Yen Kan, 
-NAACL 2017 by Margaret Mitchell, 
-ACL 2012 by Maggie Li and Michael White, 
-ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
-ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
-ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
-ACL 2002 by Eugene Charniak and Dekang Lin, 
-and earlier ACL and EACL formats written by several people, including
-John Chen, Henry S. Thompson and Donald Walker.
-Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.
 
@@
 
-The following instructions are directed to authors of papers submitted to ACL 2020 or accepted for publication in its proceedings.
-All authors are required to adhere to these specifications.
-Authors are required to provide a Portable Document Format (PDF) version of their papers.
-\textbf{The proceedings are designed for printing on A4 paper.}
+Research on metaphors, particularly in the framework of conceptual metaphor theory, continues to grow in all genres of language use and across diverse disciplines of linguistics (cf., among others, \citet{littlemore:2019:MetaphorsMindSources}; \citet{gibbsjr:2017:MetaphorWarsConceptual}; \citet{charteris-black:2016:FireMetaphorsDiscourses}; \citet{kovecses:2020:ExtendedConceptualMetaphor}; \citet{callies-degani::MetaphorLanguageCulture} for recent and forthcoming overviews and extensions, and \citet{veale-EtAl:2016:MetaphorComputationalPerspective} for a book-length discussion of computational linguistic perspectives).
+While the importance of metaphor in thought and everyday language use has long been acknowledged \citep{LakoffJohnson80}, the practice of metaphor research still faces two methodological and analytical challenges: first of all, the identification of metaphors and, secondly, their actual description through source and target domains.
 
-\section{Electronically-available resources}
+In computational linguistics, a great amount of recent work has been concerned with addressing the challenge of identifying metaphors in texts.
+This is evident in the series of four Workshops on Metaphor in NLP from 2013 to 2016 and in the two Workshops on Figurative Language Processing in 2018 and 2020, each of which involved a shared task in automatic metaphor detection.
+Identification systems that achieved the best results in the first shared task relied on neural networks incorporating LSTM architectures (see \citealp{mu-EtAl:2019} for a discussion).
+This paper extends a system proposed in \citet{stemle-onysko:2018:naacl-flpst}, which uses word-embeddings combining corpora like the BNC with the TOEFL11 language learner corpus (see \citealp{Blanchard-EtAl:TOEFL11}).
+With this system, we participate in the \emph{The Second Shared Task (ST) on Metaphor Detection}.
+The difference to the 2018 edition of the ST is a new set of data.
+As in the first task, one part of the dataset is based on the VU Amsterdam (VUA) Metaphor Corpus manually annotated according to the MIPVU procedure \citep{Steen2010}.
+Additionally, the second task includes a sample of 240 argumentative learner texts.
+These texts are taken from the ETS Corpus of Non-Native Written English (synonymous to the TOEFL11 corpus) and manually annotated \citep{beigmanklebanov-EtAl:2018}.
 
-ACL provides this description and accompanying style files at
-\begin{quote}
-\url{http://acl2020.org/downloads/acl2020-templates.zip}
-\end{quote}
-We strongly recommend the use of these style files, which have been appropriately tailored for the ACL 2020 proceedings.
+Since the learner essays are a very specific kind of data, the aim of this study is to build upon observations from \citet{stemle-onysko:2018:naacl-flpst} and further investigate factors in the data that can influence the results of neural network based metaphor identification that uses word-embeddings derived from the larger set of the same data type (the TOEFL11 corpus).
+For that, a particular focus in the training and testing is put on the metadata, specifically on proficiency, prompt and L1.
 
-\paragraph{\LaTeX-specific details:}
-The templates include the \LaTeX2e{} source (\texttt{\small acl2020.tex}),
-the \LaTeX2e{} style file used to format it (\texttt{\small acl2020.sty}),
-an ACL bibliography style (\texttt{\small acl\_natbib.bst}),
-an example bibliography (\texttt{\small acl2020.bib}),
-and the bibliography for the ACL Anthology (\texttt{\small anthology.bib}).
+To address these aims, our paper is structured as follows: Section 2 provides some observations on the annotated learner corpus dataset.
+Section 3 describes the system of metaphor identification.
+This is followed in Section 4 by the results of the experiments, which are briefly discussed in light of the observations on the annotated learner corpus data.
 
-\section{Length of Submission}
-\label{sec:length}
+\section{Observations on the data}
 
-The conference accepts submissions of long papers and short papers.
-Long papers may consist of up to eight (8) pages of content plus unlimited pages for references.
-Upon acceptance, final versions of long papers will be given one additional page -- up to nine (9) pages of content plus unlimited pages for references -- so that reviewers' comments can be taken into account.
-Short papers may consist of up to four (4) pages of content, plus unlimited pages for references.
-Upon acceptance, short papers will be given five (5) pages in the proceedings and unlimited pages for references. 
-For both long and short papers, all illustrations and tables that are part of the main text must be accommodated within these page limits, observing the formatting instructions given in the present document.
-Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.
+The VUA Metaphor Corpus and its application in the first shared task has been concisely described in \citet{leong-EtAl:2018:PFLP}.
+The authors have reported the relatively high inter-annotator agreement ($\kappa>0.8$), which is in part due to the MIPVU protocol \citep{Steen2010} and the close training of annotators in the Amsterdam Metaphor Group.
+Interestingly, the results of the first task across all submitted systems showed a clear genre bias with academic texts consistently displaying the highest correct identification rates and conversation data (i.e.~spoken texts) the lowest \citet[p.60]{leong-EtAl:2018:PFLP}.
+This might be related to the fact that academic discourse is more schematic and formulaic (e.g.~in the use sentential adverbials and verbal constructions) and might rely to a greater extent on recurrent metaphorical expressions than spoken conversations, which are less schematic and can thus display a higher degree of syntactic and lexical variation.
+In other words, similarities in the data between training and test sets might be higher in the academic than in the conversation genre, leading to different genre-specific training effects in neural networks.
 
-The conference encourages the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
-There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.
-Additional material must be submitted as separate files, and must adhere to the same anonymity guidelines as the main paper.
-The paper must be self-contained: it is optional for reviewers to look at the supplementary material.
-Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers.
-Refer to Appendices~\ref{sec:appendix} and \ref{sec:supplemental} for further information.
+Apart from the VUA metaphor corpus, the second shared task introduces a novel dataset culled from the ETS Corpus of Non-Native Written English.
+In their description, \citet{beigmanklebanov-EtAl:2018} report an average inter-annotator agreement of $\kappa=0.62$ on marking argumentation-relevant metaphors.
+Disagreement in the annotations was positively compensated in that all metaphor annotations were included even if only given by one of the two raters.
+While a focus on argumentation-relevant metaphors coheres with the genre of short argumentative learner essays written in response to one of eight prompts during TOEFL examinations in 2006-2007 \citep{ETS2:ETS202331}, the scope of metaphor annotation is more restricted in the ETS sample than in the VUA corpus, which follows the more stringent MIPVU protocol.
+This explains to some extent why the overall amount of metaphor-related words in the training sets is considerably lower in the ETS sample (an average of 7\% in All-POS and 14\% among verbs; see \citealp[p.88]{beigmanklebanov-EtAl:2018}) than in the VUA Metaphor Corpus (15\% in All-POS and 28.3\% among verbs; see Leong et al., 2018: 58).
 
-Workshop chairs may have different rules for allowed length and whether supplemental material is welcome.
-As always, the respective call for papers is the authoritative source.
+The relatively small size of the ETS sample inspired us to look into the structure of the data more closely to check whether any potential biases exist that might play a role for the automatic detection of metaphors.
+\citet[p.89]{beigmanklebanov-EtAl:2018} report a significant positive correlation of the number of metaphors and the proficiency ratings of the texts as medium or high in the data.
+This relationship is confirmed by an independent samples t-test in the training partition of the data (180 texts).
+The group of highly proficient learners ($N=95$) uses more metaphors ($M=13.98, SD=8.23$) compared to the group of medium proficient learners ($N=85, M=9.55, SD=5.96$) at a significantly higher rate ($t=4.07, p=0.000071$).
+The L1 background of the learners (i.e.
+Arabic, Italian, Japanese) did not influence the mean number of metaphors in the texts as confirmed by a one-way ANOVA ($F=1.619, p=0.201$; L1 Arabic: $N=63, M=12.48, SD=8.37$; L1 Italian: $N=59, M=12.71, SD=7.79$; L1 Japanese: $N=59, M=10.44, SD=6.38$).
 
-\section{Anonymity}
-As reviewing will be double-blind, papers submitted for review should not include any author information (such as names or affiliations).
-Furthermore, self-references that reveal the author's identity, \emph{e.g.},
-\begin{quote}
-We previously showed \citep{Gusfield:97} \ldots
-\end{quote}
-should be avoided. Instead, use citations such as 
-\begin{quote}
-\citet{Gusfield:97} previously showed\ldots
-\end{quote}
-Please do not use anonymous citations and do not include acknowledgements.
-\textbf{Papers that do not conform to these requirements may be rejected without review.}
+\begin{table}[t]
+\begin{center}
+%\small
+\begin{tabular}{|l|c|c|c|c|c|H c|}
+\hline
+    \multicolumn{1}{ |c|}{\rotatebox{90}{\textbf{Prompt}            }}		& 
+    \multicolumn{1}{ c| }{\rotatebox{90}{\# words                   }}		& 
+    \multicolumn{1}{ c| }{\rotatebox{90}{\# metaph. types              }}		& 
+    \multicolumn{1}{ c| }{\rotatebox{90}{\# metaph. tokens             }}		& 
+    \multicolumn{1}{ c| }{\rotatebox{90}{Metaph. type/toks             }} 		&
+    \multicolumn{1}{ c| }{\rotatebox{90}{\% metaph. per words        }} 		&
+    \multicolumn{1}{ H  }{\rotatebox{90}{rate of Metaph. reoccurrence\    }} 		&
+    \multicolumn{1}{ c| }{\rotatebox{90}{mean \# of metaph.}} 		\\
+\hline
+\hline
+\textbf{P1}  & 8059  & 205       & 361   & 0.57  & 4.5     & 22.3  & 15.696 \\
+\hline
 
-Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
-Reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.
+\textbf{P2}  & 7493  & 199       & 330   & 0.60  & 4.4     & 22.7  & 15.714 \\
+\hline
 
-Once a paper has been accepted to the conference, the camera-ready version of the paper should include the author's names and affiliations, and is allowed to use self-references.
+\textbf{P3}  & 7947  & 222       & 397   & 0.59  & 4.8     & 21.0  & 17.227 \\
+\hline
 
-\paragraph{\LaTeX-specific details:}
-For an anonymized submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is commented out, and that you have filled in the paper ID number (assigned during the submission process on softconf) where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top of this document.
-For a camera-ready submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is not commented out.
+\textbf{P4}  & 8076  & 146       & 173   & 0.84  & 2.1     & 46.7  & 7.522 \\
+\hline
 
-\section{Multiple Submission Policy}
-Papers that have been or will be submitted to other meetings or publications must indicate this at submission time in the START submission form, and must be withdrawn from the other venues if accepted by ACL 2020.
-Authors of papers accepted for presentation at ACL 2020 must notify the program chairs by the camera-ready deadline as to whether the paper will be presented.
-We will not accept for publication or presentation the papers that overlap significantly in content or results with papers that will be (or have been) published elsewhere.
+\textbf{P5}  & 8455  & 172       & 206   & 0.83  & 2.4     & 41.0  & 8.957 \\
+\hline
 
-Authors submitting more than one paper to ACL 2020 must ensure that submissions do not overlap significantly (>25\%) with each other in content or results.
+\textbf{P6}  & 8446  & 134       & 188   & 0.71  & 2.2     & 44.9  & 7.833 \\
+\hline
 
-\section{Formatting Instructions}
+\textbf{P7}  & 7516  & 170       & 243   & 0.70  & 3.2     & 30.9  & 11.045 \\
+\hline
 
-Manuscripts must be in two-column format.
-Exceptions to the two-column format include the title, authors' names and complete addresses, which must be centered at the top of the first page, and any full-width figures or tables (see the guidelines in Section~\ref{ssec:title-authors}).
-\textbf{Type single-spaced.}
-Start all pages directly under the top margin.
-The manuscript should be printed single-sided and its length should not exceed the maximum page limit described in Section~\ref{sec:length}.
-Pages should be numbered in the version submitted for review, but \textbf{pages should not be numbered in the camera-ready version}.
+\textbf{P8}  & 7923  & 197       & 260   & 0.76  & 3.3     & 30.4  & 11.818 \\
 
-\paragraph{\LaTeX-specific details:}
-The style files will generate page numbers when {\small\verb|\aclfinalcopy|} is commented out, and remove them otherwise.
+\hline
+\end{tabular}
+\end{center}
+\caption{\label{tab:num_metaphors}Number of metaphors (types and tokens) per prompt in the annotated ETS training set} 
+\end{table}
 
-\subsection{File Format}
-\label{sect:pdf}
+Since the Corpus of Non-Native Written English consists of argumentative learner essays that were written in response to one of eight different prompts, another factor to consider in the annotated ETS sample is the role the prompt might have on metaphor use.
+Table \ref{tab:num_metaphors} summarizes the descriptive statistics on the number of metaphors per prompt.
 
-For the production of the electronic manuscript you must use Adobe's Portable Document Format (PDF).
-Please make sure that your PDF file includes all the necessary fonts (especially tree diagrams, symbols, and fonts with Asian characters).
-When you print or create the PDF file, there is usually an option in your printer setup to include none, all or just non-standard fonts.
-Please make sure that you select the option of including ALL the fonts.
-\textbf{Before sending it, test your PDF by printing it from a computer different from the one where it was created.}
-Moreover, some word processors may generate very large PDF files, where each page is rendered as an image.
-Such images may reproduce poorly.
-In this case, try alternative ways to obtain the PDF.
-One way on some systems is to install a driver for a postscript printer, send your document to the printer specifying ``Output to a file'', then convert the file to PDF.
+From left to right, the columns in Table \ref{tab:num_metaphors} report, per prompt, the total number of words, the number of metaphor types, the overall number of metaphor tokens (i.e.
+all words annotated for metaphor), the type token ratio of metaphors, the relative amount of metaphor tokens among all words, and the mean values of metaphors.
+The two rightmost columns illustrate an uneven occurrence of metaphors across the diverse prompts.
+Three groups emerge from the data according to their similarly high (or low) values: P1, P2, P3 as the highest scoring group, P4, P5, P6 as the lowest scoring group, and P7, P8 whose values are in-between the other two groups.
+A one-way ANOVA for independent samples ($F=7.0919, p=.00001$) confirms a significant difference between the groups.
+T-tests comparing the minimal and maximal numerical distances between the high, the medium, and the low clusters show that the high cluster is significantly different from the low cluster (P1: $N=23, M=15.70, SD=8.138$ compared to P5: $N=23, M=8.96, SD=4.117$) at $t(44)=3.54, p=.000948$.
+The differences between the low and the medium groups as well as the high and the medium group do not reach a significance threshold of $p<.01$.
 
-It is of utmost importance to specify the \textbf{A4 format} (21 cm x 29.7 cm) when formatting the paper.
-Print-outs of the PDF file on A4 paper should be identical to the hardcopy version.
-If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs as soon as possible.
+When looking for an explanation of these biased metaphor occurrences, some interesting patterns emerge among the high frequency group (P1, P2, and P3).
+In all these instances, the prompts trigger certain metaphor-related words (MRW) that occur at a high rate.
+Table 2 provides an overview of the metaphorical expressions triggered by the prompts P1, P2, and P3.
+The 30 most frequent MRW were closely analyzed for each of the prompts.
 
-\paragraph{\LaTeX-specific details:}
-PDF files are usually produced from \LaTeX{} using the \texttt{\small pdflatex} command.
-If your version of \LaTeX{} produces Postscript files, \texttt{\small ps2pdf} or \texttt{\small dvipdf} can convert these to PDF.
-To ensure A4 format in \LaTeX, use the command {\small\verb|\special{papersize=210mm,297mm}|}
-in the \LaTeX{} preamble (below the {\small\verb|\usepackage|} commands) and use \texttt{\small dvipdf} and/or \texttt{\small pdflatex}; or specify \texttt{\small -t a4} when working with \texttt{\small dvips}.
+\begin{table*}[t]
+\setlength{\tabcolsep}{3pt}
+\begin{center}
+%\small
+\begin{tabularx}{\textwidth}{|X|r|X|r|X|r|}
+\hline
+    \multicolumn{6}{|>{\hsize=\dimexpr8\hsize+14\tabcolsep+2\arrayrulewidth\relax}X|}{
+        \textbf{P1:} It is better to have broad knowledge of many academic subjects than to specialize  in one specific subject.
+    }
+    \\
+    \multicolumn{6}{|X|}{}
+    \\
+    \multicolumn{6}{|>{\hsize=\dimexpr8\hsize+14\tabcolsep+2\arrayrulewidth\relax}X|}{
+        \textbf{P2:} Young people enjoy life more than older people do.
+    }
+    \\
+    \multicolumn{6}{|X|}{}
+    \\
+    \multicolumn{6}{|>{\hsize=\dimexpr8\hsize+14\tabcolsep+2\arrayrulewidth\relax}X|}{
+        \textbf{P3:} Young people nowadays do not give enough time to helping their communities.
+    }
+    \\
+\hline
+    \multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{\shortstack[l]{\textbf{metaphorical} \\ \textbf{expression}}}	
+    &
+    \shortstack[l]{\textbf{\# of} \\ \textbf{occur.}} 
+    & 
+    \multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{\shortstack[l]{\textbf{metaphorical} \\ \textbf{expression}}}
+    &
+    \shortstack[l]{\textbf{\# of} \\ \textbf{occur.}}
+    &
+    \multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{\shortstack[l]{\textbf{metaphorical} \\ \textbf{expression}}}
+    &
+    \shortstack[l]{\textbf{\# of} \\ \textbf{occur.}} 
+    \\
+\hline
+\hline
+    \multicolumn{2}{|l|}{\textbf{P1}}
+    & 
+    \multicolumn{2}{|l|}{\textbf{P2}}
+    & 
+    \multicolumn{2}{|l|}{\textbf{P3}}
+    \\
+\hline
+%%
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+\enquote{broad(er) knowledge}
+} &
+60 &
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+have/-ing/has \newline
+\enquote{have time}
+} & 
+55 & 
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+give/-s/-ing/-en \newline 
+\enquote{give time}, \enquote{give help}
+} & 
+29
+\\
+%
+\hline
+%
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+focus/-ed \newline
+\enquote{focus on a particular subject/field} 
+} &
+12 &
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+spend/-s/-ing \newline
+\enquote{spend time/hours/years} } & 
+14 & 
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+have/-ing/has \newline
+\enquote{have time}
+} & 
+24
+\\
+%
+\hline
+%
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+*give/-s/-ing 
+}		&
+10 &
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+*face \newline
+\enquote{face problems / change / responsibilities} 
+} & 
+6 & 
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+spend/-ing/-t  \newline
+\enquote{spend time}
+} & 
+16
+\\
+%
+\hline
+%
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+wide/-er 
+}		&
+9 &
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+*get 
+} & 
+5 & 
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+support/-s/-ing/-ed  \newline
+\enquote{support communities}
+} & 
+14
+\\
+%
+\hline
+%
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+*lead/-s 
+} &
+7 &
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+stage \newline
+\enquote{stage of life} 
+} & 
+4 & 
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+*strong/-er/-ly
+} & 
+14 
+\\
+%
+\hline
+%
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+*spend 
+}		&
+6 &
+ & 
+ & 
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+free \newline
+\enquote{free time}
+} & 
+9
+\\
+%
+\hline
+%
+ &
+ &
+ & 
+ & 
+\multicolumn{1}{ |>{\hsize=\dimexpr2\hsize+4\tabcolsep+\arrayrulewidth\relax}X|}{
+dedicate/-s \newline
+\enquote{dedicate time}
+} & 
+9
+\\
+%%
+\hline
+\end{tabularx}
+\end{center}
+\caption{\label{tab:frequent_metaphors}Most frequent metaphorical expressions in P1, P2, and P3 \\ 
+(*) MRW does not occur verbatim in the prompt }
+\end{table*}
 
-\subsection{Layout}
-\label{ssec:layout}
+In Table \ref{tab:frequent_metaphors}, MRW that cannot be related to the prompt are preceded by an asterisk.
+All the other terms are triggered by the prompts.
+For P1, the expression \enquote{broad knowledge} from the prompt that instantiates an objectification metaphor of knowledge (\textsc{knowledge is an object}) is frequently reiterated in the test takers’ essays and is by far the most frequent metaphorical expression among all annotated MRW in P1.
+The metaphorical uses of the lexeme \emph{focus} as in \enquote{focus on a particular subject/field} is triggered by the prompt as a synonymous phrase for \enquote{\ldots specialize in one specific subject}.
+Similarly, the term \emph{wide/-er} is used by some learners as a synonym of \enquote{broad knowledge}.
+In P2, the metaphorical phrase \enquote{have time} is prevalent.
+It is thematically triggered by the phrase \enquote{enjoy life}, which stimulates people to write about time as a (precious) possession that allows you to enjoy life.
+The metaphorical expression of \enquote{spending time} is evoked by the same conceptual metaphor.
+The \textsc{life is a journey} metaphor triggered by P2 is instantiated in the recurrent expression of stages in life.
+The mention of \enquote{time} in P3 evokes the same \textsc{time is a precious possession} conceptual metaphor as in P2.
+Again, the by far most recurrent MRW are the verbs \emph{give, have}, and \emph{spend} that objectify time in that metaphor.
+In addition, the use of the verb \emph{support} as in \enquote{support communities} is directly related to the prompt (\enquote{\ldots to helping their communities}) as are the metaphorical collocations \enquote{free time} and \enquote{dedicate time}.
 
-Format manuscripts two columns to a page, in the manner these
-instructions are formatted.
-The exact dimensions for a page on A4 paper are:
+In all the other prompts, trigger effects do not occur or are not as quantitatively relevant as in P1 to P3.
+P4, for example, does not show any spikes in metaphor frequencies with the most frequent MRW (\emph{image}) merely occurring 5 times.
+The same is true in P5 with the terms \emph{ruining, reach, comfortable}, and \emph{advancement} being mentioned 4 times each as the most frequent MRWs.
+A weak effect can be observed in P6 where the prompt \enquote{The best way to travel is in a group led by a tour guide} triggers the metaphorical collocation to \enquote{take a trip} that recurs 14 times across the learner texts.
+In P7 and P8, the most frequent MRW are not stimulated by the prompt, and there are similarly low token frequencies leading to a flat frequency distribution among the MRW.
+Incidentally, P8 (\enquote{Successful people try new things and take risks rather than only doing what they already know how to do well}) contains the metaphorical expression \enquote{take risks} that recurs in the learner essays 43 times.
+However, it has not been manually annotated as an MRW.
 
+If we take a look at how the MRW are distributed across the different parts of speech, it is interesting to note that verbs are by far more often marked as metaphors than nouns and adjectives/adverbs.
+Among the 30 most frequent MRW per prompt in the training set, 416 metaphorical verbs precede over 198 adjectives/adverbs and 141 nouns.
+
+Finally, the learner data poses another peculiarity that is worth considering in the automatic metaphor identification.
+There is a total of 99 misspelled MRW across all prompts in the data (4.6\% of all MRW) as in \emph{messege, actractivity, strenght, knowled, isolte, dangerousness}, and \emph{broadn} to randomly pick out a few.
+Finding a way to factor in the out-of-vocabulary words will increase the performance of automatic metaphor detection.
+
+\section{Design and implementation}
+
+Our approach extends the system from Stemle and Onysko (2018), which combines a small set of established machine learning (ML) methods and tools.
+In particular, the system uses fastText\footnote{\url{https://fasttext.cc/}} word embeddings from different corpora in a bi-directional recursive neural network architecture with long-term short-term memory (LSTM BiRNN) and implements a flat sequence-to-sequence neural network with one hidden layer using TensorFlow and Keras\footnote{\url{https://www.tensorflow.org/guide/keras}} in Python.
+The experimental design uses word embeddings from corpora such as Wikipedia\footnote{https://fasttext.cc/docs/en/english-vectors.html} and BNC\footnote{https://embeddings.sketchengine.co.uk/static/index.html} as well as from texts of language learners (TOEFL11, Blanchard et al.
+2013).
+This is to follow the intuition that the use of metaphors can vary depending on the competence of the learners and that these differences can be helpful in training a metaphor detection system.
+
+For the current ST, the system was slightly extended: 
+\begin{enumerate}
+\item bump requirements of used tools to current versions, in particular: TensorFlow  + Keras, gensim\footnote{\url{https://radimrehurek.com/gensim/}}, FastText, and scikit-learn\footnote{\url{https://scikit-learn.org/}}
+\item deal with the new format of the TOEFL data
+\item make better use of sub-word information encoded in FastText word representations
+\item add option to integrate metadata into the input representations for the neural network
+\end{enumerate}
+
+\section{Experiments}
+
+\subsection{Combining VUA and TOEFL}
+In a first experiment, we tried to extend the training data and combine the two datasets. 
+Given the discussion in Section 2, we expected confounding effects due to the fact that the manual classification of All-POS metaphors is different in these two sets.
+
+As word embeddings, we used BNC and the complete TOEFL11 data.
+The input data was constructed for both tasks (AllPOS and Verbs) by concatenating the test sets in both permutations. That is, first the TOEFL test set and then the VUA test set, and vice versa.
+Testing was done by 10-fold cross-validation, which only approximates the proper sequence testing of input data, but we believe this will provide us with some valuable information.
+
+Table \ref{tab:sequence_learning} shows that, most notably, the highest recall is achieved on the Verbs task when using first the TOEFL data and subsequently the VUA data.
+We interpret that in a way that the learning of the TOEFL data is mostly 'forgotten' by the neural network, but its focus on verb-metaphors leaves a strong initialization bias towards verbs.
+
+Overall, the results of the various runs show how different the two datasets are and, conversely, how much could be gained from homogeneously annotated data.
+
+Finally, we hope to be able to evaluate this experiment on the held-out test set from the organizers.
+
+% \begin{table*}[t]
+% \begin{center}
+% \begin{tabular}{lll|l|l||l|l|}
+% \cline{4-7}
+% \multicolumn{3}{l}{}                                          &  \multicolumn{4}{|c|}{Task}  \\ 
+% \cline{1-2} \cline{4-7} 
+% \multicolumn{2}{|c|}{Training}  &  & \multicolumn{2}{|c||}{Verbs} & \multicolumn{2}{c|}{AllPOS} \\ 
+% \hline 
+% \multicolumn{2}{|c|}{In order 1:VUA 2:TOEFL} &    & VUA          & TOEFL         & VUA               & TOEFL       \\ \hline \hline
+% \multicolumn{2}{|l|}{}      & Pr    & 0.48 (+/- 0.10) & 0.48 (+/- 0.08) & 0.47 (+/- 0.10)   & 0.47 (+/- 0.11) \\ \cline{3-7} 
+% \multicolumn{2}{|l|}{}      & Re    & 0.49 (+/- 0.15) & 0.49 (+/- 0.14) & 0.41 (+/- 0.10)   & 0.41 (+/- 0.11) \\ \cline{3-7} 
+% \multicolumn{2}{|l|}{}      & F1    & 0.48            & 0.48            & 0.44              & 0.44            \\ \hline \hline
+% \multicolumn{2}{|c|}{In order 1:TOEFL 2:VUA} &  \multicolumn{5}{l}{}  \\ \hline \hline 
+% \multicolumn{2}{|l|}{}      & Pr    &  0.39 (+/- 0.15) & 0.40 (+/- 0.15) & 0.32 (+/- 0.11) & 0.39 (+/- 0.23) \\ \cline{3-7}
+% \multicolumn{2}{|l|}{}      & Re    &  0.79 (+/- 0.04) & 0.77 (+/- 0.05) & 0.71 (+/- 0.24) & 0.71 (+/- 0.24) \\ \cline{3-7} 
+% \multicolumn{2}{|l|}{}      & F1    &  0.52            & 0.53            & 0.44            & 0.50            \\ \hline
+% \multicolumn{2}{|c|}{Shuffled: TOEFL + VUA} &  \multicolumn{5}{l}{}  \\ \hline \hline 
+% \multicolumn{2}{|l|}{}      & Pr    & 0.51 (+/- 0.02)  & 0.53 (+/- 0.03) & 0.52 (+/- 0.04) & 0.51 (+/- 0.03) \\ \cline{3-7}
+% \multicolumn{2}{|l|}{}      & Re    & 0.69 (+/- 0.02)  & 0.67 (+/- 0.06) & 0.66 (+/- 0.06) & 0.67 (+/- 0.04) \\ \cline{3-7} 
+% \multicolumn{2}{|l|}{}      & F1    & 0.59             & 0.59            & 0.58            & 0.58            \\ \hline
+% \end{tabular}
+% \end{center}
+% \caption{\label{tab:sequence_learning}10-fold CV comparison of training on (un)shuffled VUA and TOEFL data for the Verb and AllPOS Task.}
+% \end{table*}
+
+\begin{table}[]
+\setlength{\tabcolsep}{4.5pt}
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+\multicolumn{2}{|c|}{Training}               &    & \multicolumn{2}{c|}{Task}         \\ \hline \hline 
+\multicolumn{2}{|c|}{\shortstack[l]{In order \\ 1:VUA \\ 2:TOEFL}} &    & Verbs           & AllPOS             \\ \hline
+\multicolumn{2}{|l|}{}                       & Pr & 0.48 (+/- 0.10) & 0.47 (+/- 0.11) \\ \cline{3-5} 
+\multicolumn{2}{|l|}{}                       & Re & 0.49 (+/- 0.15) & 0.41 (+/- 0.11) \\ \cline{3-5} 
+\multicolumn{2}{|l|}{}                       & F1 & 0.48            & 0.44            \\ \hline \hline
+\multicolumn{2}{|c|}{\shortstack[l]{In order \\ 1:TOEFL \\ 2:VUA}} & \multicolumn{3}{l}{}  \\ \hline
+\multicolumn{2}{|l|}{}                       & Pr & 0.39 (+/- 0.15) & 0.39 (+/- 0.23) \\ \cline{3-5} 
+\multicolumn{2}{|l|}{}                       & Re & 0.79 (+/- 0.04) & 0.71 (+/- 0.24) \\ \cline{3-5} 
+\multicolumn{2}{|l|}{}                       & F1 & 0.52            & 0.50            \\ \hline \hline
+\multicolumn{2}{|c|}{\shortstack[l]{Shuffled \\ VUA \\ + \\ TOEFL}}  &  \multicolumn{3}{l}{}   \\ \hline
+\multicolumn{2}{|l|}{}                       & Pr & 0.51 (+/- 0.02) & 0.51 (+/- 0.03) \\ \cline{3-5} 
+\multicolumn{2}{|l|}{}                       & Re & 0.69 (+/- 0.02) & 0.67 (+/- 0.04) \\ \cline{3-5} 
+\multicolumn{2}{|l|}{}                       & F1 & 0.59            & 0.58            \\ \hline
+\end{tabular}
+\caption{\label{tab:sequence_learning}10-fold CV comparison of training on (un)shuffled VUA and TOEFL data for the Verb and AllPOS Task.}
+\end{table}
+
+% vuamc-toefl_on_vuamc-verb.eval            accuracy                                  0.97 (+/- 0.01)
+% vuamc-toefl_on_vuamc-verb.eval            precision                                 0.48 (+/- 0.10)
+% vuamc-toefl_on_vuamc-verb.eval            recall                                    0.49 (+/- 0.15)
+
+% vuamc-toefl_on_toefl-verb.eval            accuracy                                  0.97 (+/- 0.01)
+% vuamc-toefl_on_toefl-verb.eval            precision                                 0.48 (+/- 0.08)
+% vuamc-toefl_on_toefl-verb.eval            recall                                    0.49 (+/- 0.14)
+
+% vuamc-toefl_on_vuamc.eval                 accuracy                                  0.95 (+/- 0.02)
+% vuamc-toefl_on_vuamc.eval                 precision                                 0.47 (+/- 0.10)
+% vuamc-toefl_on_vuamc.eval                 recall                                    0.41 (+/- 0.10)
+
+% vuamc-toefl_on_toefl.eval                 accuracy                                  0.95 (+/- 0.02)
+% vuamc-toefl_on_toefl.eval                 precision                                 0.47 (+/- 0.11)
+% vuamc-toefl_on_toefl.eval                 recall                                    0.41 (+/- 0.11)
+
+% toefl-vuamc_on_vuamc-verb.eval            accuracy                                  0.96 (+/- 0.00)
+% toefl-vuamc_on_vuamc-verb.eval            precision                                 0.39 (+/- 0.15)
+% toefl-vuamc_on_vuamc-verb.eval            recall                                    0.79 (+/- 0.04)
+
+% toefl-vuamc_on_toefl-verb.eval            accuracy                                  0.96 (+/- 0.00)
+% toefl-vuamc_on_toefl-verb.eval            precision                                 0.40 (+/- 0.15)
+% toefl-vuamc_on_toefl-verb.eval            recall                                    0.77 (+/- 0.05)
+
+% toefl-vuamc_on_vuamc.eval                 accuracy                                  0.91 (+/- 0.01)
+% toefl-vuamc_on_vuamc.eval                 precision                                 0.32 (+/- 0.11)
+% toefl-vuamc_on_vuamc.eval                 recall                                    0.71 (+/- 0.24)
+
+% toefl-vuamc_on_toefl.eval                 accuracy                                  0.91 (+/- 0.02)
+% toefl-vuamc_on_toefl.eval                 precision                                 0.39 (+/- 0.23)
+% toefl-vuamc_on_toefl.eval                 recall                                    0.71 (+/- 0.24)
+
+% toefl-vuamc_on_vuamc-verb-shuf.eval       accuracy                                  0.97 (+/- 0.00)
+% toefl-vuamc_on_vuamc-verb-shuf.eval       precision                                 0.51 (+/- 0.02)
+% toefl-vuamc_on_vuamc-verb-shuf.eval       recall                                    0.69 (+/- 0.02)
+
+% toefl-vuamc_on_toefl-verb-shuf.eval       accuracy                                  0.98 (+/- 0.00)
+% toefl-vuamc_on_toefl-verb-shuf.eval       precision                                 0.53 (+/- 0.03)
+% toefl-vuamc_on_toefl-verb-shuf.eval       recall                                    0.67 (+/- 0.06)
+
+% toefl-vuamc_on_vuamc-shuf.eval            accuracy                                  0.95 (+/- 0.00)
+% toefl-vuamc_on_vuamc-shuf.eval            precision                                 0.52 (+/- 0.04)
+% toefl-vuamc_on_vuamc-shuf.eval            recall                                    0.66 (+/- 0.06)
+
+% toefl-vuamc_on_toefl-shuf.eval            accuracy                                  0.95 (+/- 0.00)
+% toefl-vuamc_on_toefl-shuf.eval            precision                                 0.51 (+/- 0.03)
+% toefl-vuamc_on_toefl-shuf.eval            recall                                    0.67 (+/- 0.04)
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Metadata}
+In this experiment, we added available metadata as additional information to learn from.
+The difference is that compared to other information, such as POS tags, this metadata applies to whole sentences and the entire texts.
+Also, this experiment only addresses the TOEFL dataset.
+
+The available metadata are the following:
 \begin{itemize}
-\item Left and right margins: 2.5 cm
-\item Top margin: 2.5 cm
-\item Bottom margin: 2.5 cm
-\item Column width: 7.7 cm
-\item Column height: 24.7 cm
-\item Gap between columns: 0.6 cm
+\item Prompt: The prompt that triggered the production of the respective sentence and text (P1-P8)
+\item Proficiency: The proficiency of the language learner who produced the text (medium or high)
+\item L1: The language learner's L1 (ARA, JPN, ITA)
+\item Text ID: The text's unique ID (which represents the individual language learner)
+\item Text length: The length (in tokens) of the complete text the respective sentence belongs to
 \end{itemize}
 
-\noindent Papers should not be submitted on any other paper size.
-If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.
+Given the discussion in Section 2, we expected confounding effects for some of the metadata, and we hoped to improve the results when factoring in the metadata that showed significant effects on the number and use of metaphors.
 
-\subsection{Fonts}
+As word embeddings, we used only the BNC.
+The input data was constructed for both tasks (AllPOS and Verbs) by adding the metadata information for every single word in the input sequence. 
+Testing was done by 10-fold cross-validation.
 
-For reasons of uniformity, Adobe's \textbf{Times Roman} font should be used.
-If Times Roman is unavailable, you may use Times New Roman or \textbf{Computer Modern Roman}.
+Table \ref{tab:metadata} shows that, most notably, the overall metadata does \emph{not} improve the results in a systematic, meaningful way.
+Also, some metadata, like the \emph{Text ID} even considerably degrades performance. Overall, there is no clear tendency towards metadata being more -- if at all - helpful.
 
-Table~\ref{font-table} specifies what font sizes and styles must be used for each type of text in the manuscript.
+In addition, we evaluated some combinations on the organizers' held-out test (via CodaLab) and found that the Verb task - contrary to our 10-fold CV - gained slightly from the use of metadata.
+We hope to be able to evaluate this experiment on the held-out test set from the organizers.
+Alternatively, we could split the available dataset and re-run the experiments with this data.
 
-\begin{table}
-\centering
-\begin{tabular}{lrl}
-\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
-paper title & 15 pt & bold \\
-author names & 12 pt & bold \\
-author affiliation & 12 pt & \\
-the word ``Abstract'' & 12 pt & bold \\
-section titles & 12 pt & bold \\
-subsection titles & 11 pt & bold \\
-document text & 11 pt  &\\
-captions & 10 pt & \\
-abstract text & 10 pt & \\
-bibliography & 10 pt & \\
-footnotes & 9 pt & \\
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+\setlength{\tabcolsep}{2.5pt}
+\begin{center}
+\begin{tabular}{|l|l|l|l|}
 \hline
+                                                                                   &    & Verbs           & AllPOS          \\ \hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Baseline\\ (no metadt.)\end{tabular}}  & Pr & 0.53 (+/- 0.05) & 0.53 (+/- 0.04) \\ \cline{2-4} 
+                                                                                   & Re & 0.64 (+/- 0.07) & 0.63 (+/- 0.05) \\ \hline
+\multirow{2}{*}{Prompt}                                                            & Pr & 0.50 (+/- 0.06) & 0.51 (+/- 0.05) \\ \cline{2-4} 
+                                                                                   & Re & 0.66 (+/- 0.10) & 0.64 (+/- 0.05) \\ \hline
+\multirow{2}{*}{Proficiency}                                                       & Pr & 0.51 (+/- 0.07) & 0.51 (+/- 0.05) \\ \cline{2-4} 
+                                                                                   & Re & 0.68 (+/- 0.09) & 0.65 (+/- 0.07) \\ \hline
+\multirow{2}{*}{L1}                                                                & Pr & 0.49 (+/- 0.05) & 0.53 (+/- 0.06) \\ \cline{2-4} 
+                                                                                   & Re & 0.68 (+/- 0.08) & 0.60 (+/- 0.06) \\ \hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Prom.+  \\ Prof. + L1\end{tabular}} & Pr & 0.54 (+/- 0.07) & 0.52 (+/- 0.06) \\ \cline{2-4} 
+                                                                                   & Re & 0.62 (+/- 0.07) & 0.64 (+/- 0.06) \\ \hline
+\multirow{2}{*}{Text ID}                                                           & Pr & 0.42 (+/- 0.08) & 0.48 (+/- 0.08) \\ \cline{2-4} 
+                                                                                   & Re & 0.72 (+/- 0.09) & 0.60 (+/- 0.10) \\ \hline
+\multirow{2}{*}{Text length}                                                       & Pr & 0.50 (+/- 0.06) & 0.53 (+/- 0.06) \\ \cline{2-4} 
+                                                                                   & Re & 0.66 (+/- 0.11) & 0.62 (+/- 0.05) \\ \hline
+\multirow{2}{*}{All}                                                               & Pr & 0.45 (+/- 0.08) & 0.44 (+/- 0.08) \\ \cline{2-4} 
+                                                                                   & Re & 0.68 (+/- 0.08) & 0.64 (+/- 0.08) \\ \hline
 \end{tabular}
-\caption{\label{font-table} Font guide. }
+\end{center}
+\caption{\label{tab:metadata}10-fold CV comparison of training on different metadata.}
 \end{table}
 
-\paragraph{\LaTeX-specific details:}
-To use Times Roman in \LaTeX2e{}, put the following in the preamble:
-\begin{quote}
-\small
-\begin{verbatim}
-\usepackage{times}
-\usepackage{latexsym}
-\end{verbatim}
-\end{quote}
+% toefl-all_pos-bnc.eval                    accuracy                                  0.97 (+/- 0.00)
+% toefl-all_pos-bnc.eval                    precision                                 0.53 (+/- 0.04)
+% toefl-all_pos-bnc.eval                    recall                                    0.63 (+/- 0.05)
 
-\subsection{Ruler}
-A printed ruler (line numbers in the left and right margins of the article) should be presented in the version submitted for review, so that reviewers may comment on particular lines in the paper without circumlocution.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera ready copy should not contain a ruler.
+% toefl-all_pos-bnc-meta_cat_prom.eval      accuracy                                  0.97 (+/- 0.00)
+% toefl-all_pos-bnc-meta_cat_prom.eval      precision                                 0.51 (+/- 0.05)
+% toefl-all_pos-bnc-meta_cat_prom.eval      recall                                    0.64 (+/- 0.05)
 
-\paragraph{Reviewers:}
-note that the ruler measurements may not align well with lines in the paper -- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-In most cases one would expect that the approximate location will be adequate, although you can also use fractional references (\emph{e.g.}, this line ends at mark $295.5$).
+% toefl-all_pos-bnc-meta_cat_prof.eval      accuracy                                  0.97 (+/- 0.00)
+% toefl-all_pos-bnc-meta_cat_prof.eval      precision                                 0.51 (+/- 0.05)
+% toefl-all_pos-bnc-meta_cat_prof.eval      recall                                    0.65 (+/- 0.07)
 
-\paragraph{\LaTeX-specific details:}
-The style files will generate the ruler when {\small\verb|\aclfinalcopy|} is commented out, and remove it otherwise.
+% toefl-all_pos-bnc-meta_cat_l1.eval        accuracy                                  0.97 (+/- 0.00)
+% toefl-all_pos-bnc-meta_cat_l1.eval        precision                                 0.53 (+/- 0.06)
+% toefl-all_pos-bnc-meta_cat_l1.eval        recall                                    0.60 (+/- 0.06)
 
-\subsection{Title and Authors}
-\label{ssec:title-authors}
+% toefl-all_pos-bnc-meta_cats.eval          accuracy                                  0.97 (+/- 0.00)
+% toefl-all_pos-bnc-meta_cats.eval          precision                                 0.52 (+/- 0.06)
+% toefl-all_pos-bnc-meta_cats.eval          recall                                    0.64 (+/- 0.06)
 
-Center the title, author's name(s) and affiliation(s) across both columns.
-Do not use footnotes for affiliations.
-Place the title centered at the top of the first page, in a 15-point bold font.
-Long titles should be typed on two lines without a blank line intervening.
-Put the title 2.5 cm from the top of the page, followed by a blank line, then the author's names(s), and the affiliation on the following line.
-Do not use only initials for given names (middle initials are allowed).
-Do not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not ``MITCHELL'').
-Do not format title and section headings in all capitals except for proper names (such as ``BLEU'') that are
-conventionally in all capitals.
-The affiliation should contain the author's complete address, and if possible, an electronic mail address.
+% toefl-all_pos-bnc-meta_ids.eval           accuracy                                  0.97 (+/- 0.01)
+% toefl-all_pos-bnc-meta_ids.eval           precision                                 0.48 (+/- 0.08)
+% toefl-all_pos-bnc-meta_ids.eval           recall                                    0.60 (+/- 0.10)
 
-The title, author names and addresses should be completely identical to those entered to the electronical paper submission website in order to maintain the consistency of author information among all publications of the conference.
-If they are different, the publication chairs may resolve the difference without consulting with you; so it is in your own interest to double-check that the information is consistent.
+% toefl-all_pos-bnc-meta_len.eval           accuracy                                  0.97 (+/- 0.00)
+% toefl-all_pos-bnc-meta_len.eval           precision                                 0.53 (+/- 0.06)
+% toefl-all_pos-bnc-meta_len.eval           recall                                    0.62 (+/- 0.05)
 
-Start the body of the first page 7.5 cm from the top of the page.
-\textbf{Even in the anonymous version of the paper, you should maintain space for names and addresses so that they will fit in the final (accepted) version.}
+% toefl-all_pos-bnc-meta_all.eval           accuracy                                  0.96 (+/- 0.01)
+% toefl-all_pos-bnc-meta_all.eval           precision                                 0.44 (+/- 0.08)
+% toefl-all_pos-bnc-meta_all.eval           recall                                    0.64 (+/- 0.08)
 
-\subsection{Abstract}
-Use two-column format when you begin the abstract.
-Type the abstract at the beginning of the first column.
-The width of the abstract text should be smaller than the
-width of the columns for the text in the body of the paper by 0.6 cm on each side.
-Center the word \textbf{Abstract} in a 12 point bold font above the body of the abstract.
-The abstract should be a concise summary of the general thesis and conclusions of the paper.
-It should be no longer than 200 words.
-The abstract text should be in 10 point font.
+% toefl-verb-bnc.eval                       accuracy                                  0.99 (+/- 0.00)
+% toefl-verb-bnc.eval                       precision                                 0.53 (+/- 0.05)
+% toefl-verb-bnc.eval                       recall                                    0.64 (+/- 0.07)
 
-\subsection{Text}
-Begin typing the main body of the text immediately after the abstract, observing the two-column format as shown in the present document.
+% toefl-verb-bnc-meta_cat_prom.eval         accuracy                                  0.98 (+/- 0.00)
+% toefl-verb-bnc-meta_cat_prom.eval         precision                                 0.50 (+/- 0.06)
+% toefl-verb-bnc-meta_cat_prom.eval         recall                                    0.66 (+/- 0.10)
 
-Indent 0.4 cm when starting a new paragraph.
+% toefl-verb-bnc-meta_cat_prof.eval         accuracy                                  0.99 (+/- 0.00)
+% toefl-verb-bnc-meta_cat_prof.eval         precision                                 0.51 (+/- 0.07)
+% toefl-verb-bnc-meta_cat_prof.eval         recall                                    0.68 (+/- 0.09)
 
-\subsection{Sections}
+% toefl-verb-bnc-meta_cat_l1.eval           accuracy                                  0.98 (+/- 0.00)
+% toefl-verb-bnc-meta_cat_l1.eval           precision                                 0.49 (+/- 0.05)
+% toefl-verb-bnc-meta_cat_l1.eval           recall                                    0.68 (+/- 0.08)
 
-Format section and subsection headings in the style shown on the present document.
-Use numbered sections (Arabic numerals) to facilitate cross references.
-Number subsections with the section number and the subsection number separated by a dot, in Arabic numerals.
+% toefl-verb-bnc-meta_cats.eval             accuracy                                  0.99 (+/- 0.00)
+% toefl-verb-bnc-meta_cats.eval             precision                                 0.54 (+/- 0.07)
+% toefl-verb-bnc-meta_cats.eval             recall                                    0.62 (+/- 0.07)
 
-\subsection{Footnotes}
-Put footnotes at the bottom of the page and use 9 point font.
-They may be numbered or referred to by asterisks or other symbols.\footnote{This is how a footnote should appear.}
-Footnotes should be separated from the text by a line.\footnote{Note the line separating the footnotes from the text.}
+% toefl-verb-bnc-meta_ids.eval              accuracy                                  0.98 (+/- 0.00)
+% toefl-verb-bnc-meta_ids.eval              precision                                 0.42 (+/- 0.08)
+% toefl-verb-bnc-meta_ids.eval              recall                                    0.72 (+/- 0.09)
 
-\subsection{Graphics}
+% toefl-verb-bnc-meta_len.eval              accuracy                                  0.98 (+/- 0.00)
+% toefl-verb-bnc-meta_len.eval              precision                                 0.50 (+/- 0.06)
+% toefl-verb-bnc-meta_len.eval              recall                                    0.66 (+/- 0.11)
 
-Place figures, tables, and photographs in the paper near where they are first discussed, rather than at the end, if possible.
-Wide illustrations may run across both columns.
-Color is allowed, but adhere to Section~\ref{ssec:accessibility}'s guidelines on accessibility.
+% toefl-verb-bnc-meta_all.eval              accuracy                                  0.98 (+/- 0.01)
+% toefl-verb-bnc-meta_all.eval              precision                                 0.45 (+/- 0.08)
+% toefl-verb-bnc-meta_all.eval              recall                                    0.68 (+/- 0.08)
 
-\paragraph{Captions:}
-Provide a caption for every illustration; number each one sequentially in the form:
-``Figure 1. Caption of the Figure.''
-``Table 1. Caption of the Table.''
-Type the captions of the figures and tables below the body, using 10 point text.
-Captions should be placed below illustrations.
-Captions that are one line are centered (see Table~\ref{font-table}).
-Captions longer than one line are left-aligned (see Table~\ref{tab:accents}).
+%- Vergleich: BNC vs BNC + NLI
 
-\begin{table}
-\centering
-\begin{tabular}{lc}
-\hline
-\textbf{Command} & \textbf{Output}\\
-\hline
-\verb|{\"a}| & {\"a} \\
-\verb|{\^e}| & {\^e} \\
-\verb|{\`i}| & {\`i} \\ 
-\verb|{\.I}| & {\.I} \\ 
-\verb|{\o}| & {\o} \\
-\verb|{\'u}| & {\'u}  \\ 
-\verb|{\aa}| & {\aa}  \\\hline
-\end{tabular}
-\begin{tabular}{lc}
-\hline
-\textbf{Command} & \textbf{Output}\\
-\hline
-\verb|{\c c}| & {\c c} \\ 
-\verb|{\u g}| & {\u g} \\ 
-\verb|{\l}| & {\l} \\ 
-\verb|{\~n}| & {\~n} \\ 
-\verb|{\H o}| & {\H o} \\ 
-\verb|{\v r}| & {\v r} \\ 
-\verb|{\ss}| & {\ss} \\
-\hline
-\end{tabular}
-\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
-\end{table}
+\section{Conclusion}
 
-\paragraph{\LaTeX-specific details:}
-The style files are compatible with the caption and subcaption packages; do not add optional arguments.
-\textbf{Do not override the default caption sizes.}
+This paper has focused on the structure of the learner data used in the Second Shared Task of Metaphor Identification.
+We aimed at exploring possible factors that influence this kind of data and tested whether these play a role for the automated identification using word-embeddings in an LSTM BiRNN architecture.
+A descriptive investigation of the manually annotated sample of the ETS Corpus of Non-Native Written English (TOEFL11 corpus) shows that the factors of proficiency and especially the essay prompt exhibit significant correlations to the amount and type of metaphors found in the annotated training set.
+The data also shows a numerical bias towards the annotation of verbs as metaphors compared to other content words.
 
-\subsection{Hyperlinks}
-Within-document and external hyperlinks are indicated with Dark Blue text, Color Hex \#000099.
-
-\subsection{Citations}
-Citations within the text appear in parentheses as~\citep{Gusfield:97} or, if the author's name appears in the text itself, as \citet{Gusfield:97}.
-Append lowercase letters to the year in cases of ambiguities.  
-Treat double authors as in~\citep{Aho:72}, but write as in~\citep{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\citep{Gusfield:97,Aho:72}.
-
-Refrain from using full citations as sentence constituents.
-Instead of
-\begin{quote}
-  ``\citep{Gusfield:97} showed that ...''
-\end{quote}
-write
-\begin{quote}
-``\citet{Gusfield:97} showed that ...''
-\end{quote}
-
-\begin{table*}
-\centering
-\begin{tabular}{lll}
-\hline
-\textbf{Output} & \textbf{natbib command} & \textbf{Old ACL-style command}\\
-\hline
-\citep{Gusfield:97} & \small\verb|\citep| & \small\verb|\cite| \\
-\citealp{Gusfield:97} & \small\verb|\citealp| & no equivalent \\
-\citet{Gusfield:97} & \small\verb|\citet| & \small\verb|\newcite| \\
-\citeyearpar{Gusfield:97} & \small\verb|\citeyearpar| & \small\verb|\shortcite| \\
-\hline
-\end{tabular}
-\caption{\label{citation-guide}
-Citation commands supported by the style file.
-The style is based on the natbib package and supports all natbib citation commands.
-It also supports commands defined in previous ACL style files for compatibility.
-}
-\end{table*}
-
-\paragraph{\LaTeX-specific details:}
-Table~\ref{citation-guide} shows the syntax supported by the style files.
-We encourage you to use the natbib styles.
-You can use the command {\small\verb|\citet|} (cite in text) to get ``author (year)'' citations as in \citet{Gusfield:97}.
-You can use the command {\small\verb|\citep|} (cite in parentheses) to get ``(author, year)'' citations as in \citep{Gusfield:97}.
-You can use the command {\small\verb|\citealp|} (alternative cite without  parentheses) to get ``author year'' citations (which is useful for  using citations within parentheses, as in \citealp{Gusfield:97}).
-
-\subsection{References}
-Gather the full set of references together under the heading \textbf{References}; place the section before any Appendices. 
-Arrange the references alphabetically by first author, rather than by order of occurrence in the text.
-
-Provide as complete a citation as possible, using a consistent format, such as the one for \emph{Computational Linguistics\/} or the one in the  \emph{Publication Manual of the American 
-Psychological Association\/}~\citep{APA:83}.
-Use full names for authors, not just initials.
-
-Submissions should accurately reference prior and related work, including code and data.
-If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
-If multiple versions of a piece of prior work exist, the one used by the authors should be referenced.
-Authors should not rely on automated citation indices to provide accurate references for prior and related work.
-
-The following text cites various types of articles so that the references section of the present document will include them.
-\begin{itemize}
-\item Example article in journal: \citep{Ando2005}.
-\item Example article in proceedings, with location: \citep{borschinger-johnson-2011-particle}.
-\item Example article in proceedings, without location: \citep{andrew2007scalable}.
-\item Example arxiv paper: \citep{rasooli-tetrault-2015}. 
-\end{itemize}
-
-\paragraph{\LaTeX-specific details:}
-The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
-If your own bib file is named \texttt{\small acl2020.bib}, then placing the following before any appendices in your \LaTeX{}  file will generate the references section for you:
-\begin{quote}\small
-\verb|\bibliographystyle{acl_natbib}|\\
-\verb|\bibliography{acl2020}|
-\end{quote}
-
-You can obtain the complete ACL Anthology as a Bib\TeX\ file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
-To include both the anthology and your own bib file, use the following instead of the above.
-\begin{quote}\small
-\verb|\bibliographystyle{acl_natbib}|\\
-\verb|\bibliography{anthology,acl2020}|
-\end{quote}
-
-\subsection{Digital Object Identifiers}
-As part of our work to make ACL materials more widely used and cited outside of our discipline, ACL has registered as a CrossRef member, as a registrant of Digital Object Identifiers (DOIs), the standard for registering permanent URNs for referencing scholarly materials.
-
-All camera-ready references are required to contain the appropriate DOIs (or as a second resort, the hyperlinked ACL Anthology Identifier) to all cited works.
-Appropriate records should be found for most materials in the current ACL Anthology at \url{http://aclanthology.info/}.
-As examples, we cite \citep{goodman-etal-2016-noise} to show you how papers with a DOI will appear in the bibliography.
-We cite \citep{harper-2014-learning} to show how papers without a DOI but with an ACL Anthology Identifier will appear in the bibliography.
-
-\paragraph{\LaTeX-specific details:}
-Please ensure that you use Bib\TeX\ records that contain DOI or URLs for any of the ACL materials that you reference.
-If the Bib\TeX{} file contains DOI fields, the paper title in the references section will appear as a hyperlink to the DOI, using the hyperref \LaTeX{} package.
-
-\subsection{Appendices}
-Appendices, if any, directly follow the text and the
-references (but only in the camera-ready; see Appendix~\ref{sec:appendix}).
-Letter them in sequence and provide an informative title:
-\textbf{Appendix A. Title of Appendix}.
-
-\section{Accessibility}
-\label{ssec:accessibility}
-
-In an effort to accommodate people who are color-blind (as well as those printing to paper), grayscale readability is strongly encouraged.
-Color is not forbidden, but authors should ensure that tables and figures do not rely solely on color to convey critical distinctions.
-A simple criterion:
-All curves and points in your figures should be clearly distinguishable without color.
-
-\section{Translation of non-English Terms}
-
-It is also advised to supplement non-English characters and terms with appropriate transliterations and/or translations since not all readers understand all such characters and terms.
-Inline transliteration or translation can be represented in the order of:
-\begin{center}
-\begin{tabular}{c}
-original-form \\
-transliteration \\
-``translation''
-\end{tabular}
-\end{center}
-
-\section{\LaTeX{} Compilation Issues}
-You may encounter the following error during compilation: 
-\begin{quote}
-{\small\verb|\pdfendlink|} ended up in different nesting level than {\small\verb|\pdfstartlink|}.
-\end{quote}
-This happens when \texttt{\small pdflatex} is used and a citation splits across a page boundary.
-To fix this, the style file contains a patch consisting of two lines:
-(1) {\small\verb|\RequirePackage{etoolbox}|} (line 455 in \texttt{\small acl2020.sty}), and
-(2) A long line below (line 456 in \texttt{\small acl2020.sty}).
-
-If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \texttt{\small hyperref} package by loading the style file with the \texttt{\small nohyperref} option:
-
-\noindent
-{\small\verb|\usepackage[nohyperref]{acl2020}|}
-
-\noindent
-Then recompile, find the problematic citation, and rewrite the sentence containing the citation. (See, {\em e.g.}, \url{http://tug.org/errors.html})
+ A sequential training of the bidirectional neural network using both the VUA and the TOEFL partitions of the shared task points to the different structure of the datasets, in particular towards an emerging bias of overidentifying verbal metaphors in the neural network based classification.
+The hypothesized influence of the metadata in the TOEFL set, in particular the observed dependencies on proficiency and the essay prompt, was not confirmed by the results of the automated identification.
+While the factors of L1, proficiency, prompt and essay length did not influence the baseline results, the essay ID (i.e.
+the individual learner) reduced the performance of the system as did a combination of all metadata.
+For the future, more tests with different ways of modelling the metadata in the neural network architecture and on the test set of the task will provide further insights.
 
 \section*{Acknowledgments}
+The computational results presented have been achieved in part using the \href{http://vsc.ac.at}{Vienna Scientific Cluster (VSC)}.
 
-The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
-Do not include this section when submitting your paper for review.
-
-Attributions.
-In the event that Researcher produces a written work that incorporates the
-Results or limited excerpts of the Data (with prior written consent from ETS),
-Researcher agrees to acknowledge the Data as property of ETS by displaying the
-following attributions:
-
-Source: 
-Derived from data provided by ETS. Copyright \textcopyright{}2020 ETS,
-\url{www.ets.org}.
-
-Disclaimer.
-Researcher must also include the following disclaimer language in all publications:  
-The opinions set forth in this publication are those of the author(s) and not ETS.
-
-\bibliography{anthology,acl2020}
+%\section*{References}
+%\leftskip 0.15in%
+%\parindent -0.15in%
+%\setlength{\parskip}{7pt}% 
+%\noindent
+%
+%
+\bibliography{anthology,acl2020,egon}
 \bibliographystyle{acl_natbib}
-
-\appendix
-
-\section{Appendices}
-\label{sec:appendix}
-Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
-Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
-Upon acceptance, the appendices come after the references, as shown here.
-
-\paragraph{\LaTeX-specific details:}
-Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
-
-\section{Supplemental Material}
-\label{sec:supplemental}
-Submissions may include non-readable supplementary material used in the work and described in the paper.
-Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
-Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
-Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
-
-Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
-\textbf{Submissions that misuse the supplementary material may be rejected without review.}
-Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
-features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
-(Source code and data should be separate uploads, rather than part of the paper).
-
-The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.
-
 \end{document}

### 2020-05-25 paper.tex
Update on Overleaf.

@@
 \usepackage[utf8x]{inputenc}
-\usepackage[autostyle=none]{csquotes}
+\usepackage[english]{babel}
+\usepackage[autostyle=tryonce]{csquotes}
 \usepackage{tabularx}
@@
 
-%\aclfinalcopy % Uncomment this line for the final submission
+\aclfinalcopy % Uncomment this line for the final submission
 %\def\aclpaperid{***} %  Enter the acl Paper ID here
@@
 
-\title{Testing the role of metadata in a neural network architecture of metaphor identification}
+\title{Testing the role of metadata in metaphor identification}
 
@@
 
+% ============================================================================
+% REVIEWER #1
+% ============================================================================
+%
+% ---------------------------------------------------------------------------
+% Reviewer's Scores
+% ---------------------------------------------------------------------------
+%                    Appropriateness (1-5): 5
+%                            Clarity (1-5): 4
+%       Originality / Innovativeness (1-5): 3
+%            Soundness / Correctness (1-5): 3
+%              Meaningful Comparison (1-5): 1
+%                       Thoroughness (1-5): 2
+%         Impact of Ideas or Results (1-5): 3
+%                     Recommendation (1-5): 2
+%                Reviewer Confidence (1-5): 4
+%
+% Detailed Comments
+% ---------------------------------------------------------------------------
+% 1.
+The main contribution of this paper is to demonstrate the difference between the two datasets through training by merging the two datasets and to explore the influence of metadata on the effect of metaphor detection.
+However, in general, the contribution is insufficient, because the difference between the two datasets is not an important discovery, and metadata does not seem to improve the effect of metaphor detection very well.
+% Reply: We have made the objective of our study clearer in the introduction.
+% 2.
+The metadata discussed in this paper is limited to external features such as proficiency, native language type, text ID, and so on, which seem to have little relevance to metaphor.
+It is more valuable to explore the deep linguistic features such as lexical, syntactic, and semantic features related to metaphor.
+% Reply: The clarification of the study’s aims now provides an answer to the question of why it makes sense to explore the relevance of the metadata - based on findings in previous research. 
+% [introduction / conclusion: express more clearly what the paper does and what not]
+% 3. It is better to define alphabetic symbols in the paper, such as L1, M, SD, F, so that readers who do not participate in the sharing task can understand.
+% Reply: the abbreviation L1 has been defined.
+The other abbreviations that the reviewer mentions are standard notations for reporting statistical results and, as such, it is not necessary and would actually be highly unusual to spell them out.
+% 4. The introduction of related research work in this paper is not enough, there are some latest related papers.
+% Reply: Four relevant papers have been added in the introduction.
+% 5. The format of Table 3 is not standard and the sixth reference is in the wrong format.
+% Reply: fixed
+% 6. Other mistakes: line 120: in the use (of), line 403: In a first experiment
+% Reply: fixed
+%
+% ---------------------------------------------------------------------------
+
+% ============================================================================
+%                             REVIEWER #2
+% ============================================================================
+%
+% ---------------------------------------------------------------------------
+% Reviewer's Scores
+% ---------------------------------------------------------------------------
+%                   Appropriateness (1-5): 5
+%                           Clarity (1-5): 3
+%       Originality / Innovativeness (1-5): 3
+%           Soundness / Correctness (1-5): 3
+%              Meaningful Comparison (1-5): 2
+%                       Thoroughness (1-5): 4
+%         Impact of Ideas or Results (1-5): 3
+%                     Recommendation (1-5): 3
+%               Reviewer Confidence (1-5): 3
+%
+% Detailed Comments
+% ---------------------------------------------------------------------------
+% This paper studies the word-level metaphor detection with a focus on the structure of training data.
+It extends the metaphor detection system from (Stemle and Onysko, 2018).
+It is built upon a bi-directional recursive neural network with long-short term memory, using fastText word embeddings and metadata information.
+% Some interesting empirical finds are made in this work: 
+% (1) When the model is trained on the combination of VUA and TOEFL data, the shuffling of data achieves performance gains.
+% (2) The metadata information does not improve the metaphor detection performance.
+%
+% 1. Formatting
+% (1) Can authors put the header horizontally in Table 1 for better readability?
+%Reply: we believe this would waste a lot of space (table would have to span two columns), and that the readability is ok-ish
+% (2) Missing right table boundaries in Table 3.
+%Reply: fixed
+% (3) F1 scores are missing in Table 4, which are better included for an easy comparison between different metadata types.
+%Reply: fixed
+%
+% 2.
+Model.
+It is a novel idea to incorporate metadata information into the model training based on the interesting observations described in Section 2.
+But it needs more details about how the metadata information is used.
+%Reply: added description in the Design and implementation section 
+%
+% 2.
+Experiment results.
+What results are reported in Table 3 and 4?
+Are these test results for VUA, TOEFL or both?
+Also Table 3 includes results on verbs, are results in Table 4 on verbs or all POS tags?
+For the completeness of empirical results, it would be better to report all results on all POS and verbs respectively as well as on VUA and TOEFL data respectively.
+%Reply: Table 3 now reports results for VUA and TOEFL; Table 4 reports data on TOEFL (because we only have metadata for TOEFL) and this has been made explicit in the caption
+% 2.
+Related works.
+Although some studies on metaphor detection are mentioned in Introduction, some more related works are worth mentioning to provide the readers with necessary background information.
+%Reply: Four more relevant papers have been added in the introduction.
+%
+% [Egon: network systems/ Alex: more references from overview paper]
+% ---------------------------------------------------------------------------
+
 \begin{document}
@@
 \begin{abstract}
-This paper describes the application of a neural network for the automatic detection of metaphors.
-The system participated in the shared task of metaphor identification that is part of the Second Workshop of Figurative Language Processing held at ACL 2020.
+This paper describes the adaptation and application of a neural network system for the automatic detection of metaphors.
+The  LSTM BiRNN system participated in the shared task of metaphor identification that was part of the Second Workshop of Figurative Language Processing (FigLang2020) held at the Annual Conference of the Association for Computational Linguistics (ACL2020).
 The particular focus of our approach is on the potential influence that the metadata given in the ETS Corpus of Non-Native Written English might have on the automatic detection of metaphors in this dataset.
 The article first discusses the annotated ETS learner data, highlighting some of its peculiarities and inherent biases of metaphor use.
-This is followed by a series of evaluations performed by an LSTM BiRNN classification architecture in order to test whether specific metadata have an influence on the system performance in this task of automated metaphor identification.
+A series of evaluations follow in order to test whether specific metadata influence the system performance in the task of automatic metaphor identification.
+The system is available under the APLv2 open-source license.
 \end{abstract}
@@
 
-Research on metaphors, particularly in the framework of conceptual metaphor theory, continues to grow in all genres of language use and across diverse disciplines of linguistics (cf., among others, \citet{littlemore:2019:MetaphorsMindSources}; \citet{gibbsjr:2017:MetaphorWarsConceptual}; \citet{charteris-black:2016:FireMetaphorsDiscourses}; \citet{kovecses:2020:ExtendedConceptualMetaphor}; \citet{callies-degani::MetaphorLanguageCulture} for recent and forthcoming overviews and extensions, and \citet{veale-EtAl:2016:MetaphorComputationalPerspective} for a book-length discussion of computational linguistic perspectives).
+Research on metaphors, particularly in the framework of conceptual metaphor theory, continues to grow in all genres of language use and across diverse disciplines of linguistics (cf., among others, \citealp{littlemore:2019:MetaphorsMindSources}; \citealp{gibbsjr:2017:MetaphorWarsConceptual}; \citealp{charteris-black:2016:FireMetaphorsDiscourses}; \citealp{kovecses:2020:ExtendedConceptualMetaphor}; \citealp{callies-degani::MetaphorLanguageCulture} for recent and forthcoming overviews and extensions, and \citealp{veale-EtAl:2016:MetaphorComputationalPerspective} for a book-length discussion of computational linguistic perspectives).
 While the importance of metaphor in thought and everyday language use has long been acknowledged \citep{LakoffJohnson80}, the practice of metaphor research still faces two methodological and analytical challenges: first of all, the identification of metaphors and, secondly, their actual description through source and target domains.
@@
 In computational linguistics, a great amount of recent work has been concerned with addressing the challenge of identifying metaphors in texts.
-This is evident in the series of four Workshops on Metaphor in NLP from 2013 to 2016 and in the two Workshops on Figurative Language Processing in 2018 and 2020, each of which involved a shared task in automatic metaphor detection.
-Identification systems that achieved the best results in the first shared task relied on neural networks incorporating LSTM architectures (see \citealp{mu-EtAl:2019} for a discussion).
-This paper extends a system proposed in \citet{stemle-onysko:2018:naacl-flpst}, which uses word-embeddings combining corpora like the BNC with the TOEFL11 language learner corpus (see \citealp{Blanchard-EtAl:TOEFL11}).
-With this system, we participate in the \emph{The Second Shared Task (ST) on Metaphor Detection}.
+This is evident in the series of four Workshops on Metaphor in NLP from 2013 to 2016 and in the two Workshops on Figurative Language Processing in 2018 \citep{ws-2018} and 2020 \citep{leong2020}, each of which involved a shared task (ST) in automatic metaphor detection.
+Identification systems that achieved the best results in the first shared task relied on neural networks incorporating long-term short-term memory (LSTM) architectures (see \citealp{mu-EtAl:2019} for a discussion).
+Further advances in the field using deep learning approaches have been reported in \citet{dankers-etal-2019-modelling}, \citet{gao-etal-2018-neural-metaphor}, and \citet{rei-etal-2017}.
+
+This paper extends a system proposed in \citet{stemle-onysko:2018:naacl-flpst}, which combines word embeddings (WEs) of corpora like the BNC \citep{BNC:2007} and the TOEFL11 language learner corpus (see \citealp{Blanchard-EtAl:TOEFL11}).
+With the modified system, we participated in \emph{The Second Shared Task on Metaphor Detection}.
 The difference to the 2018 edition of the ST is a new set of data.
@@
 Additionally, the second task includes a sample of 240 argumentative learner texts.
-These texts are taken from the ETS Corpus of Non-Native Written English (synonymous to the TOEFL11 corpus) and manually annotated \citep{beigmanklebanov-EtAl:2018}.
+These texts are taken from the ETS Corpus of Non-Native Written English (synonymous to the TOEFL11 corpus) and have been manually annotated \citep{beigmanklebanov-EtAl:2018}.
 
-Since the learner essays are a very specific kind of data, the aim of this study is to build upon observations from \citet{stemle-onysko:2018:naacl-flpst} and further investigate factors in the data that can influence the results of neural network based metaphor identification that uses word-embeddings derived from the larger set of the same data type (the TOEFL11 corpus).
-For that, a particular focus in the training and testing is put on the metadata, specifically on proficiency, prompt and L1.
+Since the learner essays are a very specific kind of data, the aim of this study is to build upon observations from \citet{stemle-onysko:2018:naacl-flpst}, who found that a combination of word embeddings from the BNC and the TOEFL11 learner corpus yielded the best results of metaphor identification in a bi-directional recursive neural network (BiRNN) with LSTM.
+These results triggered the hypothesis that learner language can lead to an information gain for neural network based metaphor identification.
+To explore this hypothesis further, the current study puts an explicit focus on the metadata provided for the ETS Corpus of Non-Native Written English and specifically tests the potential influence of proficiency ratings, essay prompt, and the first language (L1) of the author.
+In addition, we also test whether a combined training on the diverse datasets and the sequence of this training will have an impact on our system of neural network based metaphor identification.
 
-To address these aims, our paper is structured as follows: Section 2 provides some observations on the annotated learner corpus dataset.
+To address these aims, our paper is structured as follows: Section 2 provides observations on the annotated learner corpus dataset.
 Section 3 describes the system of metaphor identification.
@@
 Interestingly, the results of the first task across all submitted systems showed a clear genre bias with academic texts consistently displaying the highest correct identification rates and conversation data (i.e.~spoken texts) the lowest \citet[p.60]{leong-EtAl:2018:PFLP}.
-This might be related to the fact that academic discourse is more schematic and formulaic (e.g.~in the use sentential adverbials and verbal constructions) and might rely to a greater extent on recurrent metaphorical expressions than spoken conversations, which are less schematic and can thus display a higher degree of syntactic and lexical variation.
+This might be related to the fact that academic discourse is more schematic and formulaic (e.g.~in the use of sentential adverbials and verbal constructions) and might rely to a greater extent on recurrent metaphorical expressions than spoken conversations, which are less schematic and can thus display a higher degree of syntactic and lexical variation.
 In other words, similarities in the data between training and test sets might be higher in the academic than in the conversation genre, leading to different genre-specific training effects in neural networks.
@@
 Disagreement in the annotations was positively compensated in that all metaphor annotations were included even if only given by one of the two raters.
-While a focus on argumentation-relevant metaphors coheres with the genre of short argumentative learner essays written in response to one of eight prompts during TOEFL examinations in 2006-2007 \citep{ETS2:ETS202331}, the scope of metaphor annotation is more restricted in the ETS sample than in the VUA corpus, which follows the more stringent MIPVU protocol.
-This explains to some extent why the overall amount of metaphor-related words in the training sets is considerably lower in the ETS sample (an average of 7\% in All-POS and 14\% among verbs; see \citealp[p.88]{beigmanklebanov-EtAl:2018}) than in the VUA Metaphor Corpus (15\% in All-POS and 28.3\% among verbs; see Leong et al., 2018: 58).
+While a focus on argumentation-relevant metaphors coheres with the genre of short argumentative learner essays written in response to one of eight prompts during TOEFL examinations in 2006-2007 \citep{Blanchard-EtAl:TOEFL11}, the scope of metaphor annotation is more restricted in the ETS sample than in the VUA corpus, which follows the more stringent MIPVU protocol.
+This explains to some extent why the overall amount of metaphor-related words in the training sets is considerably lower in the ETS sample (an average of 7\% in All-POS and 14\% among verbs; see \citealp[p.88]{beigmanklebanov-EtAl:2018}) than in the VUA Metaphor Corpus (15\% in All-POS and 28.3\% among verbs; see \citealp[p.58]{leong-EtAl:2018:PFLP}).
 
@@
 The group of highly proficient learners ($N=95$) uses more metaphors ($M=13.98, SD=8.23$) compared to the group of medium proficient learners ($N=85, M=9.55, SD=5.96$) at a significantly higher rate ($t=4.07, p=0.000071$).
-The L1 background of the learners (i.e.
-Arabic, Italian, Japanese) did not influence the mean number of metaphors in the texts as confirmed by a one-way ANOVA ($F=1.619, p=0.201$; L1 Arabic: $N=63, M=12.48, SD=8.37$; L1 Italian: $N=59, M=12.71, SD=7.79$; L1 Japanese: $N=59, M=10.44, SD=6.38$).
+The L1 background of the learners (i.e.~Arabic, Italian, Japanese) did not influence the mean number of metaphors in the texts as confirmed by a one-way ANOVA ($F=1.619, p=0.201$; L1 Arabic: $N=63, M=12.48, SD=8.37$; L1 Italian: $N=59, M=12.71, SD=7.79$; L1 Japanese: $N=59, M=10.44, SD=6.38$).
 
-\begin{table}[t]
+\begin{table}[htb!]
 \begin{center}
@@
 \end{center}
-\caption{\label{tab:num_metaphors}Number of metaphors (types and tokens) per prompt in the annotated ETS training set} 
+\caption{\label{tab:num_metaphors}Number of metaphors (types and tokens) per prompt in the annotated ETS training set.} 
 \end{table}
@@
 
-From left to right, the columns in Table \ref{tab:num_metaphors} report, per prompt, the total number of words, the number of metaphor types, the overall number of metaphor tokens (i.e.
-all words annotated for metaphor), the type token ratio of metaphors, the relative amount of metaphor tokens among all words, and the mean values of metaphors.
+From left to right, the columns in Table \ref{tab:num_metaphors} report, per prompt, the total number of words, the number of metaphor types, the overall number of metaphor tokens (i.e.~all words annotated for metaphor), the type token ratio of metaphors, the relative amount of metaphor tokens among all words, and the mean values of metaphors.
 The two rightmost columns illustrate an uneven occurrence of metaphors across the diverse prompts.
@@
 
-\begin{table*}[t]
+\begin{table*}[tb!]
 \setlength{\tabcolsep}{3pt}
@@
 \end{center}
-\caption{\label{tab:frequent_metaphors}Most frequent metaphorical expressions in P1, P2, and P3 \\ 
+\caption{\label{tab:frequent_metaphors}Most frequent metaphorical expressions in P1, P2, and P3. \\ 
 (*) MRW does not occur verbatim in the prompt }
@@
 P4, for example, does not show any spikes in metaphor frequencies with the most frequent MRW (\emph{image}) merely occurring 5 times.
-The same is true in P5 with the terms \emph{ruining, reach, comfortable}, and \emph{advancement} being mentioned 4 times each as the most frequent MRWs.
+The same is true in P5 with the terms \emph{ruining, reach, comfortable}, and \emph{advancement} being mentioned 4 times each as the most frequent MRW.
 A weak effect can be observed in P6 where the prompt \enquote{The best way to travel is in a group led by a tour guide} triggers the metaphorical collocation to \enquote{take a trip} that recurs 14 times across the learner texts.
@@
 Incidentally, P8 (\enquote{Successful people try new things and take risks rather than only doing what they already know how to do well}) contains the metaphorical expression \enquote{take risks} that recurs in the learner essays 43 times.
-However, it has not been manually annotated as an MRW.
+However, it has not been manually annotated as an MRW in the ETS Corpus.
 
@@
 
-Our approach extends the system from Stemle and Onysko (2018), which combines a small set of established machine learning (ML) methods and tools.
-In particular, the system uses fastText\footnote{\url{https://fasttext.cc/}} word embeddings from different corpora in a bi-directional recursive neural network architecture with long-term short-term memory (LSTM BiRNN) and implements a flat sequence-to-sequence neural network with one hidden layer using TensorFlow and Keras\footnote{\url{https://www.tensorflow.org/guide/keras}} in Python.
-The experimental design uses word embeddings from corpora such as Wikipedia\footnote{https://fasttext.cc/docs/en/english-vectors.html} and BNC\footnote{https://embeddings.sketchengine.co.uk/static/index.html} as well as from texts of language learners (TOEFL11, Blanchard et al.
-2013).
+Our approach extends the system from \citet{stemle-onysko:2018:naacl-flpst}, which combines a small set of established machine learning (ML) methods and tools.
+In particular, the system uses fastText\footnote{\url{https://fasttext.cc/}} word embeddings from different corpora in a bi-directional recursive neural network architecture with long-term short-term memory (LSTM BiRNN) and implements a flat sequence-to-sequence neural network with one hidden layer using TensorFlow+Keras \citep{tensorflow2015-whitepaper} in Python.
+With the goals we introduced in Section 1, it seemed sufficient to use a successful system from the last ST instead of improving the overall system by integrating the latest, highly successful\footnote{The current development of increasing the complexity in neural network architectures by adding more processing layers in systems comes with the trade-off of loosing insights into the mechanisms of how the improvements are achieved.~See~also~\citet{mikolov:2020:ComplexitySimplicityMachine-talk}.} developments from the field of NLP (see, e.g., \citealp{wang-EtAl:2020:StaticDynamicWord} for an overview).
+
+In their experimental design \citet{stemle-onysko:2018:naacl-flpst} use word embeddings from corpora such as Wikipedia\footnote{\url{https://fasttext.cc/docs/en/english-vectors.html}} and BNC\footnote{\url{https://embeddings.sketchengine.co.uk/static/index.html}} as well as from texts of language learners (TOEFL11).
 This is to follow the intuition that the use of metaphors can vary depending on the competence of the learners and that these differences can be helpful in training a metaphor detection system.
 
-For the current ST, the system was slightly extended: 
-\begin{enumerate}
-\item bump requirements of used tools to current versions, in particular: TensorFlow  + Keras, gensim\footnote{\url{https://radimrehurek.com/gensim/}}, FastText, and scikit-learn\footnote{\url{https://scikit-learn.org/}}
-\item deal with the new format of the TOEFL data
-\item make better use of sub-word information encoded in FastText word representations
-\item add option to integrate metadata into the input representations for the neural network
-\end{enumerate}
+For the current ST, the system was slightly extended. We
+\begin{itemize}
+\item bumped the requirements of the used tools to current versions (in particular for TensorFlow+Keras, gensim\footnote{\url{https://radimrehurek.com/gensim/}}, FastText, and scikit-learn\footnote{\url{https://scikit-learn.org/}}),
+\item adapted the system to the new format of the TOEFL data set,
+\item improved the use of sub-word information encoded in FastText word representations 
+(we fixed a bug that prevented the system to use proper subword character n-gram representations in some cases), and
+\item added an option to integrate metadata into the input representations for the neural network.
+\end{itemize}
+
+For the last point, we adapted the way the input for the neural network is represented: 
+The number of input layers corresponds to the number of features, i.e.~for multiple features, e.g.~multiple WE models or additional PoS tags, sequences are concatenated on the word level such that the number of features for an individual word grows.
+For the metadata, we added an input layer with the number of dimensions varying with the number of encoded metadata.
+
+We maintain the implementation in a source code repository\footnote{\url{https://github.com/bot-zen/}}.
+The system is available under the APLv2 open-source license.
 
@@
 \subsection{Combining VUA and TOEFL}
-In a first experiment, we tried to extend the training data and combine the two datasets. 
-Given the discussion in Section 2, we expected confounding effects due to the fact that the manual classification of All-POS metaphors is different in these two sets.
+In our first experiment, we tried to extend the training data and combine the two available datasets. 
+Given the discussion in Section 2, we expected confounding effects due to the fact that the manual classification of the All-POS- and Verb-metaphors are different in these two sets.
 
+First, we shuffled both datasets individually and then combined them in three ways: A re-shuffled combination of the two sets and two combinations where we put one set at the beginning and the other one at the end.
+For the evaluation we emulated a 10-fold CV, with training on combinations of the original datasets and testing on a held out part of one of the datasets: We trained on one of our combined sets and tested on one of 10 parts of the uncombined dataset, which had been held out from the training, and repeated this for all 10 parts.
 As word embeddings, we used BNC and the complete TOEFL11 data.
-The input data was constructed for both tasks (AllPOS and Verbs) by concatenating the test sets in both permutations. That is, first the TOEFL test set and then the VUA test set, and vice versa.
-Testing was done by 10-fold cross-validation, which only approximates the proper sequence testing of input data, but we believe this will provide us with some valuable information.
 
-Table \ref{tab:sequence_learning} shows that, most notably, the highest recall is achieved on the Verbs task when using first the TOEFL data and subsequently the VUA data.
-We interpret that in a way that the learning of the TOEFL data is mostly 'forgotten' by the neural network, but its focus on verb-metaphors leaves a strong initialization bias towards verbs.
+Table \ref{tab:sequence_learning} shows that, most notably, the highest recall is achieved on the Verbs task when using first the VUA data and subsequently the TOEFL data, and testing on the TOEFL data.
+We interpret that in a way that the learning of the VUA data is mostly 'forgotten' by the neural network, but its focus on Verb-metaphors leaves a strong initialization bias towards verbs.
 
-Overall, the results of the various runs show how different the two datasets are and, conversely, how much could be gained from homogeneously annotated data.
+Overall, the results of the various runs show that the much larger VUA data dominates the learnt properties of the model, and that the matching focus on Verb-metaphors in both datasets improves recall.
 
-Finally, we hope to be able to evaluate this experiment on the held-out test set from the organizers.
+\begin{table*}[tb!]
+\begin{center}
+\begin{tabular}{lll||l|l||l|l|}
+\hline 
+\multicolumn{2}{|c|}{}  &  & \multicolumn{2}{|c||}{Test on VUA} & \multicolumn{2}{c|}{Test on TOEFL} \\  
+\hline 
+\multicolumn{2}{|c|}{Training} &    & Verbs   & All-POS       & Verbs      & All-POS    \\ \hline \hline
+%
+\multicolumn{2}{|c|}{Shuffled}      & Pr    & \textbf{0.58 (+/- 0.03)}  & 0.55 (+/- 0.04) & 0.46 (+/- 0.09) & 0.42 (+/- 0.04) \\ \cline{3-7}
+\multicolumn{2}{|c|}{VUA + TOEFL}   & Re    & 0.65 (+/- 0.03)  & 0.64 (+/- 0.05) & 0.69 (+/- 0.07) & 0.67 (+/- 0.07) \\ \cline{3-7} 
+\multicolumn{2}{|l|}{}              & F1    & \textbf{0.61 (+/- 0.02)}  & 0.59 (+/- 0.02) & 0.54 (+/- 0.06) & 0.52 (+/- 0.03) \\ 
+\hline  \hline
+%
+\multicolumn{2}{|c|}{Sequential}    & Pr    & 0.56 (+/- 0.05) & 0.55 (+/- 0.06)  & 0.43 (+/- 0.06) & 0.44 (+/- 0.04) \\ \cline{3-7} 
+\multicolumn{2}{|c|}{1:VUA 2:TOEFL} & Re    & 0.67 (+/- 0.06) & 0.64 (+/- 0.09)  & \textbf{0.71 (+/- 0.07)} & 0.68 (+/- 0.04) \\ \cline{3-7} 
+\multicolumn{2}{|l|}{}              & F1    & 0.60 (+/- 0.03) & 0.58 (+/- 0.03)  & 0.53 (+/- 0.04) & 0.53 (+/- 0.03) \\ 
+\hline \hline
+%
+\multicolumn{2}{|c|}{Sequential}    & Pr    &  0.56 (+/- 0.04) & 0.53 (+/- 0.06) & 0.46 (+/- 0.06) & 0.42 (+/- 0.05) \\ \cline{3-7}
+\multicolumn{2}{|c|}{1:TOEFL 2:VUA} & Re    &  0.68 (+/- 0.04) & 0.67 (+/- 0.08) & 0.69 (+/- 0.08) & 0.70 (+/- 0.06) \\ \cline{3-7} 
+\multicolumn{2}{|l|}{}              & F1    &  0.61 (+/- 0.03) & 0.59 (+/- 0.02) & 0.55 (+/- 0.05) & 0.52 (+/- 0.04) \\ 
+\hline
+\hline
+\hline
+%
+\multicolumn{2}{|c|}{Baseline:}      & Pr    &  0.55 (+/- 0.04) & 0.55 (+/- 0.03) & 0.57 (+/- 0.07) & 0.53 (+/- 0.06) \\ \cline{3-7}
+\multicolumn{2}{|c|}{VUA and TOEFL} & Re    &  0.69 (+/- 0.04) & 0.68 (+/- 0.04) & 0.63 (+/- 0.08) & 0.68 (+/- 0.06) \\ \cline{3-7} 
+\multicolumn{2}{|c|}{individually}  & F1    &  0.61 (+/- 0.01) & 0.61 (+/- 0.01) & 0.59 (+/- 0.03) & 0.59 (+/- 0.03) \\ 
+\hline
+\end{tabular}
+\end{center}
+\caption{\label{tab:sequence_learning}10-fold CV comparison of training on (un)shuffled VUA and TOEFL data for the Verbs and All-POS Tasks.}
+\end{table*}
 
-% \begin{table*}[t]
-% \begin{center}
-% \begin{tabular}{lll|l|l||l|l|}
-% \cline{4-7}
-% \multicolumn{3}{l}{}                                          &  \multicolumn{4}{|c|}{Task}  \\ 
-% \cline{1-2} \cline{4-7} 
-% \multicolumn{2}{|c|}{Training}  &  & \multicolumn{2}{|c||}{Verbs} & \multicolumn{2}{c|}{AllPOS} \\ 
+%%%
+% shuffled verb on vuamc
+% 0.58 (+/- 0.03) 0.65 (+/- 0.03) 0.61 (+/- 0.02)
+% shuffled all_pos on vuamc
+% 0.55 (+/- 0.04) 0.64 (+/- 0.05) 0.59 (+/- 0.02)
+% shuffled verb on toefl
+% 0.46 (+/- 0.09) 0.69 (+/- 0.07) 0.54 (+/- 0.06)
+% shuffled all_pos on toefl
+% 0.42 (+/- 0.04) 0.67 (+/- 0.07) 0.52 (+/- 0.03)
+%%%
+% vuamc-toefl verb on vuamc
+% 0.56 (+/- 0.05) 0.67 (+/- 0.06) 0.60 (+/- 0.03)
+% vuamc-toefl all_pos on vuamc
+% 0.55 (+/- 0.06) 0.64 (+/- 0.09) 0.58 (+/- 0.03)
+% vuamc-toefl verb on toefl
+% 0.43 (+/- 0.06) 0.71 (+/- 0.07) 0.53 (+/- 0.04)
+% vuamc-toefl all_pos on toefl
+% 0.44 (+/- 0.04) 0.68 (+/- 0.04) 0.53 (+/- 0.03)
+%%%
+% toefl-vuamc verb on vuamc
+% 0.56 (+/- 0.04) 0.68 (+/- 0.04) 0.61 (+/- 0.03)
+% toefl-vuamc all_pos on vuamc
+% 0.53 (+/- 0.06) 0.67 (+/- 0.08) 0.59 (+/- 0.02)
+% toefl-vuamc verb on toefl
+% 0.46 (+/- 0.06) 0.69 (+/- 0.08) 0.55 (+/- 0.05)
+% toefl-vuamc all_pos on toefl
+% 0.42 (+/- 0.05) 0.70 (+/- 0.06) 0.52 (+/- 0.04)
+%%%
+% vuamc-shuff_on_vuamc-verb.eval
+% 0.55 (+/- 0.04) 0.69 (+/- 0.04) 0.61 (+/- 0.01)
+% vuamc-shuff_on_vuamc-all_pos.eval
+% 0.55 (+/- 0.03) 0.68 (+/- 0.04) 0.61 (+/- 0.01)
+% toefl-shuff_on_toefl-verb.eval
+% 0.57 (+/- 0.07) 0.63 (+/- 0.08) 0.59 (+/- 0.03)
+% toefl-shuff_on_toefl-all_pos.eval
+% 0.53 (+/- 0.06) 0.68 (+/- 0.06) 0.59 (+/- 0.03)
+
+% \begin{table}[htb!]
+% \setlength{\tabcolsep}{4.5pt}
+% \begin{tabular}{|l|l|l|l|l|}
 % \hline
-% \multicolumn{2}{|c|}{In order 1:VUA 2:TOEFL} &    & VUA          & TOEFL         & VUA               & TOEFL       \\ \hline \hline
-% \multicolumn{2}{|l|}{}      & Pr    & 0.48 (+/- 0.10) & 0.48 (+/- 0.08) & 0.47 (+/- 0.10)   & 0.47 (+/- 0.11) \\ \cline{3-7} 
-% \multicolumn{2}{|l|}{}      & Re    & 0.49 (+/- 0.15) & 0.49 (+/- 0.14) & 0.41 (+/- 0.10)   & 0.41 (+/- 0.11) \\ \cline{3-7} 
-% \multicolumn{2}{|l|}{}      & F1    & 0.48            & 0.48            & 0.44              & 0.44            \\ \hline \hline
-% \multicolumn{2}{|c|}{In order 1:TOEFL 2:VUA} &  \multicolumn{5}{l}{}  \\ \hline \hline 
-% \multicolumn{2}{|l|}{}      & Pr    &  0.39 (+/- 0.15) & 0.40 (+/- 0.15) & 0.32 (+/- 0.11) & 0.39 (+/- 0.23) \\ \cline{3-7}
-% \multicolumn{2}{|l|}{}      & Re    &  0.79 (+/- 0.04) & 0.77 (+/- 0.05) & 0.71 (+/- 0.24) & 0.71 (+/- 0.24) \\ \cline{3-7} 
-% \multicolumn{2}{|l|}{}      & F1    &  0.52            & 0.53            & 0.44            & 0.50            \\ \hline
-% \multicolumn{2}{|c|}{Shuffled: TOEFL + VUA} &  \multicolumn{5}{l}{}  \\ \hline \hline 
-% \multicolumn{2}{|l|}{}      & Pr    & 0.51 (+/- 0.02)  & 0.53 (+/- 0.03) & 0.52 (+/- 0.04) & 0.51 (+/- 0.03) \\ \cline{3-7}
-% \multicolumn{2}{|l|}{}      & Re    & 0.69 (+/- 0.02)  & 0.67 (+/- 0.06) & 0.66 (+/- 0.06) & 0.67 (+/- 0.04) \\ \cline{3-7} 
-% \multicolumn{2}{|l|}{}      & F1    & 0.59             & 0.59            & 0.58            & 0.58            \\ \hline
+% \multicolumn{2}{|c|}{Training}               &    & \multicolumn{2}{c|}{Task}         \\ \hline \hline 
+% \multicolumn{2}{|c|}{\shortstack[l]{In order \\ 1:VUA \\ 2:TOEFL}} &    & Verbs           & All-POS             \\ \hline
+% \multicolumn{2}{|l|}{}                       & Pr & 0.48 (+/- 0.10) & 0.47 (+/- 0.11) \\ \cline{3-5} 
+% \multicolumn{2}{|l|}{}                       & Re & 0.49 (+/- 0.15) & 0.41 (+/- 0.11) \\ \cline{3-5} 
+% \multicolumn{2}{|l|}{}                       & F1 & 0.48            & 0.44            \\ \hline \hline
+% \multicolumn{2}{|c|}{\shortstack[l]{In order \\ 1:TOEFL \\ 2:VUA}} & \multicolumn{3}{l|}{}  \\ \hline
+% \multicolumn{2}{|l|}{}                       & Pr & 0.39 (+/- 0.15) & 0.39 (+/- 0.23) \\ \cline{3-5} 
+% \multicolumn{2}{|l|}{}                       & Re & 0.79 (+/- 0.04) & 0.71 (+/- 0.24) \\ \cline{3-5} 
+% \multicolumn{2}{|l|}{}                       & F1 & 0.52            & 0.50            \\ \hline \hline
+% \multicolumn{2}{|c|}{\shortstack[l]{Shuffled \\ VUA \\ + \\ TOEFL}}  &  \multicolumn{3}{l|}{}   \\ \hline
+% \multicolumn{2}{|l|}{}                       & Pr & 0.51 (+/- 0.02) & 0.51 (+/- 0.03) \\ \cline{3-5} 
+% \multicolumn{2}{|l|}{}                       & Re & 0.69 (+/- 0.02) & 0.67 (+/- 0.04) \\ \cline{3-5} 
+% \multicolumn{2}{|l|}{}                       & F1 & 0.59            & 0.58            \\ \hline
 % \end{tabular}
-% \end{center}
-% \caption{\label{tab:sequence_learning}10-fold CV comparison of training on (un)shuffled VUA and TOEFL data for the Verb and AllPOS Task.}
-% \end{table*}
-
-\begin{table}[]
-\setlength{\tabcolsep}{4.5pt}
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-\multicolumn{2}{|c|}{Training}               &    & \multicolumn{2}{c|}{Task}         \\ \hline \hline 
-\multicolumn{2}{|c|}{\shortstack[l]{In order \\ 1:VUA \\ 2:TOEFL}} &    & Verbs           & AllPOS             \\ \hline
-\multicolumn{2}{|l|}{}                       & Pr & 0.48 (+/- 0.10) & 0.47 (+/- 0.11) \\ \cline{3-5} 
-\multicolumn{2}{|l|}{}                       & Re & 0.49 (+/- 0.15) & 0.41 (+/- 0.11) \\ \cline{3-5} 
-\multicolumn{2}{|l|}{}                       & F1 & 0.48            & 0.44            \\ \hline \hline
-\multicolumn{2}{|c|}{\shortstack[l]{In order \\ 1:TOEFL \\ 2:VUA}} & \multicolumn{3}{l}{}  \\ \hline
-\multicolumn{2}{|l|}{}                       & Pr & 0.39 (+/- 0.15) & 0.39 (+/- 0.23) \\ \cline{3-5} 
-\multicolumn{2}{|l|}{}                       & Re & 0.79 (+/- 0.04) & 0.71 (+/- 0.24) \\ \cline{3-5} 
-\multicolumn{2}{|l|}{}                       & F1 & 0.52            & 0.50            \\ \hline \hline
-\multicolumn{2}{|c|}{\shortstack[l]{Shuffled \\ VUA \\ + \\ TOEFL}}  &  \multicolumn{3}{l}{}   \\ \hline
-\multicolumn{2}{|l|}{}                       & Pr & 0.51 (+/- 0.02) & 0.51 (+/- 0.03) \\ \cline{3-5} 
-\multicolumn{2}{|l|}{}                       & Re & 0.69 (+/- 0.02) & 0.67 (+/- 0.04) \\ \cline{3-5} 
-\multicolumn{2}{|l|}{}                       & F1 & 0.59            & 0.58            \\ \hline
-\end{tabular}
-\caption{\label{tab:sequence_learning}10-fold CV comparison of training on (un)shuffled VUA and TOEFL data for the Verb and AllPOS Task.}
-\end{table}
+% \caption{\label{tab:sequence_learning}10-fold CV comparison of training on (un)shuffled VUA and TOEFL data for the Verb and All-POS Task.}
+% \end{table}
 
@@
 As word embeddings, we used only the BNC.
-The input data was constructed for both tasks (AllPOS and Verbs) by adding the metadata information for every single word in the input sequence. 
+The input data was constructed for both tasks (All-POS and Verbs) by adding the metadata information for every single word in the input sequence. 
 Testing was done by 10-fold cross-validation.
@@
 
-In addition, we evaluated some combinations on the organizers' held-out test (via CodaLab) and found that the Verb task - contrary to our 10-fold CV - gained slightly from the use of metadata.
-We hope to be able to evaluate this experiment on the held-out test set from the organizers.
-Alternatively, we could split the available dataset and re-run the experiments with this data.
+The complete held-out test set was not available at the time of writing, but we had evaluated some combinations of metadata during the shared task (via CodaLab) and found that the Verbs task - contrary to our 10-fold CV - gained slightly from the use of metadata.
+An evaluation on the complete test set would have been preferable.
+Additionally, representing the metadata at the level of the entire sequence instead of for each word individually could also noticeably influence the results.
 
@@
 % \usepackage{multirow}
-\begin{table}[]
+\begin{table}[htb!]
 \setlength{\tabcolsep}{2.5pt}
@@
 \hline
-                                                                                   &    & Verbs           & AllPOS          \\ \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Baseline\\ (no metadt.)\end{tabular}}  & Pr & 0.53 (+/- 0.05) & 0.53 (+/- 0.04) \\ \cline{2-4} 
-                                                                                   & Re & 0.64 (+/- 0.07) & 0.63 (+/- 0.05) \\ \hline
-\multirow{2}{*}{Prompt}                                                            & Pr & 0.50 (+/- 0.06) & 0.51 (+/- 0.05) \\ \cline{2-4} 
-                                                                                   & Re & 0.66 (+/- 0.10) & 0.64 (+/- 0.05) \\ \hline
-\multirow{2}{*}{Proficiency}                                                       & Pr & 0.51 (+/- 0.07) & 0.51 (+/- 0.05) \\ \cline{2-4} 
-                                                                                   & Re & 0.68 (+/- 0.09) & 0.65 (+/- 0.07) \\ \hline
-\multirow{2}{*}{L1}                                                                & Pr & 0.49 (+/- 0.05) & 0.53 (+/- 0.06) \\ \cline{2-4} 
-                                                                                   & Re & 0.68 (+/- 0.08) & 0.60 (+/- 0.06) \\ \hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Prom.+  \\ Prof. + L1\end{tabular}} & Pr & 0.54 (+/- 0.07) & 0.52 (+/- 0.06) \\ \cline{2-4} 
-                                                                                   & Re & 0.62 (+/- 0.07) & 0.64 (+/- 0.06) \\ \hline
-\multirow{2}{*}{Text ID}                                                           & Pr & 0.42 (+/- 0.08) & 0.48 (+/- 0.08) \\ \cline{2-4} 
-                                                                                   & Re & 0.72 (+/- 0.09) & 0.60 (+/- 0.10) \\ \hline
-\multirow{2}{*}{Text length}                                                       & Pr & 0.50 (+/- 0.06) & 0.53 (+/- 0.06) \\ \cline{2-4} 
-                                                                                   & Re & 0.66 (+/- 0.11) & 0.62 (+/- 0.05) \\ \hline
-\multirow{2}{*}{All}                                                               & Pr & 0.45 (+/- 0.08) & 0.44 (+/- 0.08) \\ \cline{2-4} 
-                                                                                   & Re & 0.68 (+/- 0.08) & 0.64 (+/- 0.08) \\ \hline
+                                                                                   &    & Verbs           & All-POS          \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}Baseline\\ (no metadt.)\end{tabular}}   & Pr & 0.53 (+/- 0.04) & 0.53 (+/- 0.04) \\ \cline{2-4} 
+                                                                                   & Re & 0.64 (+/- 0.07) & 0.63 (+/- 0.05) \\ \cline{2-4}
+                                                                                   & F1 & 0.57 (+/- 0.02) & 0.57 (+/- 0.03) \\ \hline
+\multirow{3}{*}{Prompt}                                                            & Pr & 0.50 (+/- 0.06) & 0.51 (+/- 0.05) \\ \cline{2-4} 
+                                                                                   & Re & 0.66 (+/- 0.10) & 0.64 (+/- 0.05) \\ \cline{2-4}
+                                                                                   & F1 & 0.56 (+/- 0.02) & 0.56 (+/- 0.03) \\ \hline
+\multirow{3}{*}{Proficiency}                                                       & Pr & 0.51 (+/- 0.07) & 0.51 (+/- 0.05) \\ \cline{2-4} 
+                                                                                   & Re & 0.68 (+/- 0.09) & 0.65 (+/- 0.07) \\ \cline{2-4}
+                                                                                   & F1 & 0.57 (+/- 0.02) & 0.57 (+/- 0.04) \\ \hline
+\multirow{3}{*}{L1}                                                                & Pr & 0.49 (+/- 0.05) & 0.53 (+/- 0.06) \\ \cline{2-4} 
+                                                                                   & Re & 0.68 (+/- 0.08) & 0.60 (+/- 0.06) \\ \cline{2-4}
+                                                                                   & F1 & 0.57 (+/- 0.02) & 0.56 (+/- 0.03) \\ \hline
+\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}Prom.+  \\ Prof. + L1\end{tabular}}     & Pr & 0.54 (+/- 0.07) & 0.52 (+/- 0.06) \\ \cline{2-4} 
+                                                                                   & Re & 0.62 (+/- 0.07) & 0.64 (+/- 0.05) \\ \cline{2-4}
+                                                                                   & F1 & 0.57 (+/- 0.03) & 0.57 (+/- 0.03) \\ \hline
+\multirow{3}{*}{Text ID}                                                           & Pr & 0.42 (+/- 0.08) & 0.48 (+/- 0.08) \\ \cline{2-4} 
+                                                                                   & Re & 0.72 (+/- 0.08) & 0.60 (+/- 0.10) \\ \cline{2-4}
+                                                                                   & F1 & 0.52 (+/- 0.05) & 0.52 (+/- 0.03) \\ \hline
+\multirow{3}{*}{Text length}                                                       & Pr & 0.50 (+/- 0.06) & 0.53 (+/- 0.05) \\ \cline{2-4} 
+                                                                                   & Re & 0.66 (+/- 0.11) & 0.62 (+/- 0.05) \\ \cline{2-4}
+                                                                                   & F1 & 0.56 (+/- 0.03) & 0.57 (+/- 0.03) \\ \hline
+\multirow{3}{*}{All}                                                               & Pr & 0.45 (+/- 0.07) & 0.44 (+/- 0.08) \\ \cline{2-4} 
+                                                                                   & Re & 0.68 (+/- 0.08) & 0.64 (+/- 0.08) \\ \cline{2-4}
+                                                                                   & F1 & 0.54 (+/- 0.04) & 0.51 (+/- 0.04) \\ \hline
 \end{tabular}
 \end{center}
-\caption{\label{tab:metadata}10-fold CV comparison of training on different metadata.}
+\caption{\label{tab:metadata}10-fold CV comparison of training with different metadata on the TOEFL dataset.}
 \end{table}
 
-% toefl-all_pos-bnc.eval                    accuracy                                  0.97 (+/- 0.00)
-% toefl-all_pos-bnc.eval                    precision                                 0.53 (+/- 0.04)
-% toefl-all_pos-bnc.eval                    recall                                    0.63 (+/- 0.05)
+% for TASK in verb all_pos; do for DATA in toefl-$TASK-bnc.eval toefl-$TASK-bnc-meta_cat_prom.eval toefl-$TASK-bnc-meta_cat_prof.eva
+% l toefl-$TASK-bnc-meta_cat_l1.eval toefl-$TASK-bnc-meta_cats.eval toefl-$TASK-bnc-meta_ids.eval toefl-$TASK-bnc-meta_len.eval toefl-$TASK-bnc-meta_all.eval  ; do echo $TASK $DATA;
+%  cat experiments/2020/20200422_meta/$DATA | grep -vE "/" | grep loss | cut -f7-8 | sed -e 's/[a-z]\+://g' | awk -v OFS='\t' '{print $1,$2,((2*$1*$2)/($1+$2))}' | ./metaeval.py ; done; done
+% verb toefl-verb-bnc.eval
+% 0.53 (+/- 0.04) 0.64 (+/- 0.07) 0.57 (+/- 0.02)
+% verb toefl-verb-bnc-meta_cat_prom.eval
+% 0.50 (+/- 0.06) 0.66 (+/- 0.10) 0.56 (+/- 0.02)
+% verb toefl-verb-bnc-meta_cat_prof.eval
+% 0.51 (+/- 0.07) 0.68 (+/- 0.09) 0.57 (+/- 0.02)
+% verb toefl-verb-bnc-meta_cat_l1.eval
+% 0.49 (+/- 0.05) 0.68 (+/- 0.08) 0.57 (+/- 0.02)
+% verb toefl-verb-bnc-meta_cats.eval
+% 0.54 (+/- 0.07) 0.62 (+/- 0.07) 0.57 (+/- 0.03)
+% verb toefl-verb-bnc-meta_ids.eval
+% 0.42 (+/- 0.08) 0.72 (+/- 0.08) 0.52 (+/- 0.05)
+% verb toefl-verb-bnc-meta_len.eval
+% 0.50 (+/- 0.06) 0.66 (+/- 0.11) 0.56 (+/- 0.03)
+% verb toefl-verb-bnc-meta_all.eval
+% 0.45 (+/- 0.07) 0.68 (+/- 0.08) 0.54 (+/- 0.04)
+% all_pos toefl-all_pos-bnc.eval
+% 0.53 (+/- 0.04) 0.63 (+/- 0.05) 0.57 (+/- 0.03)
+% all_pos toefl-all_pos-bnc-meta_cat_prom.eval
+% 0.51 (+/- 0.05) 0.64 (+/- 0.05) 0.56 (+/- 0.03)
+% all_pos toefl-all_pos-bnc-meta_cat_prof.eval
+% 0.51 (+/- 0.05) 0.65 (+/- 0.07) 0.57 (+/- 0.04)
+% all_pos toefl-all_pos-bnc-meta_cat_l1.eval
+% 0.53 (+/- 0.06) 0.60 (+/- 0.06) 0.56 (+/- 0.03)
+% all_pos toefl-all_pos-bnc-meta_cats.eval
+% 0.52 (+/- 0.06) 0.64 (+/- 0.05) 0.57 (+/- 0.03)
+% all_pos toefl-all_pos-bnc-meta_ids.eval
+% 0.48 (+/- 0.08) 0.60 (+/- 0.10) 0.52 (+/- 0.03)
+% all_pos toefl-all_pos-bnc-meta_len.eval
+% 0.53 (+/- 0.06) 0.62 (+/- 0.05) 0.57 (+/- 0.03)
+% all_pos toefl-all_pos-bnc-meta_all.eval
+% 0.44 (+/- 0.08) 0.64 (+/- 0.08) 0.51 (+/- 0.04)
 
-% toefl-all_pos-bnc-meta_cat_prom.eval      accuracy                                  0.97 (+/- 0.00)
-% toefl-all_pos-bnc-meta_cat_prom.eval      precision                                 0.51 (+/- 0.05)
-% toefl-all_pos-bnc-meta_cat_prom.eval      recall                                    0.64 (+/- 0.05)
-
-% toefl-all_pos-bnc-meta_cat_prof.eval      accuracy                                  0.97 (+/- 0.00)
-% toefl-all_pos-bnc-meta_cat_prof.eval      precision                                 0.51 (+/- 0.05)
-% toefl-all_pos-bnc-meta_cat_prof.eval      recall                                    0.65 (+/- 0.07)
-
-% toefl-all_pos-bnc-meta_cat_l1.eval        accuracy                                  0.97 (+/- 0.00)
-% toefl-all_pos-bnc-meta_cat_l1.eval        precision                                 0.53 (+/- 0.06)
-% toefl-all_pos-bnc-meta_cat_l1.eval        recall                                    0.60 (+/- 0.06)
-
-% toefl-all_pos-bnc-meta_cats.eval          accuracy                                  0.97 (+/- 0.00)
-% toefl-all_pos-bnc-meta_cats.eval          precision                                 0.52 (+/- 0.06)
-% toefl-all_pos-bnc-meta_cats.eval          recall                                    0.64 (+/- 0.06)
-
-% toefl-all_pos-bnc-meta_ids.eval           accuracy                                  0.97 (+/- 0.01)
-% toefl-all_pos-bnc-meta_ids.eval           precision                                 0.48 (+/- 0.08)
-% toefl-all_pos-bnc-meta_ids.eval           recall                                    0.60 (+/- 0.10)
-
-% toefl-all_pos-bnc-meta_len.eval           accuracy                                  0.97 (+/- 0.00)
-% toefl-all_pos-bnc-meta_len.eval           precision                                 0.53 (+/- 0.06)
-% toefl-all_pos-bnc-meta_len.eval           recall                                    0.62 (+/- 0.05)
-
-% toefl-all_pos-bnc-meta_all.eval           accuracy                                  0.96 (+/- 0.01)
-% toefl-all_pos-bnc-meta_all.eval           precision                                 0.44 (+/- 0.08)
-% toefl-all_pos-bnc-meta_all.eval           recall                                    0.64 (+/- 0.08)
-
-% toefl-verb-bnc.eval                       accuracy                                  0.99 (+/- 0.00)
-% toefl-verb-bnc.eval                       precision                                 0.53 (+/- 0.05)
-% toefl-verb-bnc.eval                       recall                                    0.64 (+/- 0.07)
-
-% toefl-verb-bnc-meta_cat_prom.eval         accuracy                                  0.98 (+/- 0.00)
-% toefl-verb-bnc-meta_cat_prom.eval         precision                                 0.50 (+/- 0.06)
-% toefl-verb-bnc-meta_cat_prom.eval         recall                                    0.66 (+/- 0.10)
-
-% toefl-verb-bnc-meta_cat_prof.eval         accuracy                                  0.99 (+/- 0.00)
-% toefl-verb-bnc-meta_cat_prof.eval         precision                                 0.51 (+/- 0.07)
-% toefl-verb-bnc-meta_cat_prof.eval         recall                                    0.68 (+/- 0.09)
-
-% toefl-verb-bnc-meta_cat_l1.eval           accuracy                                  0.98 (+/- 0.00)
-% toefl-verb-bnc-meta_cat_l1.eval           precision                                 0.49 (+/- 0.05)
-% toefl-verb-bnc-meta_cat_l1.eval           recall                                    0.68 (+/- 0.08)
-
-% toefl-verb-bnc-meta_cats.eval             accuracy                                  0.99 (+/- 0.00)
-% toefl-verb-bnc-meta_cats.eval             precision                                 0.54 (+/- 0.07)
-% toefl-verb-bnc-meta_cats.eval             recall                                    0.62 (+/- 0.07)
-
-% toefl-verb-bnc-meta_ids.eval              accuracy                                  0.98 (+/- 0.00)
-% toefl-verb-bnc-meta_ids.eval              precision                                 0.42 (+/- 0.08)
-% toefl-verb-bnc-meta_ids.eval              recall                                    0.72 (+/- 0.09)
-
-% toefl-verb-bnc-meta_len.eval              accuracy                                  0.98 (+/- 0.00)
-% toefl-verb-bnc-meta_len.eval              precision                                 0.50 (+/- 0.06)
-% toefl-verb-bnc-meta_len.eval              recall                                    0.66 (+/- 0.11)
-
-% toefl-verb-bnc-meta_all.eval              accuracy                                  0.98 (+/- 0.01)
-% toefl-verb-bnc-meta_all.eval              precision                                 0.45 (+/- 0.08)
-% toefl-verb-bnc-meta_all.eval              recall                                    0.68 (+/- 0.08)
-
-%- Vergleich: BNC vs BNC + NLI
+%- FIXME: Compare BNC vs BNC + NLI
 
@@
 This paper has focused on the structure of the learner data used in the Second Shared Task of Metaphor Identification.
-We aimed at exploring possible factors that influence this kind of data and tested whether these play a role for the automated identification using word-embeddings in an LSTM BiRNN architecture.
+We aimed at exploring possible factors that influence this kind of data and tested whether these play a role for the automated identification using word embeddings in an established LSTM BiRNN system from the first ST in 2018.
 A descriptive investigation of the manually annotated sample of the ETS Corpus of Non-Native Written English (TOEFL11 corpus) shows that the factors of proficiency and especially the essay prompt exhibit significant correlations to the amount and type of metaphors found in the annotated training set.
-The data also shows a numerical bias towards the annotation of verbs as metaphors compared to other content words.
+The data also show a numerical bias towards the annotation of verbs as metaphors compared to other content words.
 
@@
 The hypothesized influence of the metadata in the TOEFL set, in particular the observed dependencies on proficiency and the essay prompt, was not confirmed by the results of the automated identification.
-While the factors of L1, proficiency, prompt and essay length did not influence the baseline results, the essay ID (i.e.
-the individual learner) reduced the performance of the system as did a combination of all metadata.
+While the factors of L1, proficiency, prompt and essay length did not influence the baseline results, the essay ID (i.e.~the individual learner) reduced the performance of the system as did a combination of all metadata.
 For the future, more tests with different ways of modelling the metadata in the neural network architecture and on the test set of the task will provide further insights.
@@
 %
+%\pagebreak
 \bibliography{anthology,acl2020,egon}
